\subsection{Unlocking SSTV Magic: Ideal Receivers for DRM!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E2B09] What kind of receiver can be used to receive and decode SSTV using the Digital Radio Mondiale (DRM) protocol?
    \begin{enumerate}[label=\Alph*,noitemsep]
        \item CDMA
        \item AREDN
        \item AM
        \item \textbf{SSB}
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a special kind of radio that can pick up pictures sent over the air. These pictures are called SSTV (Slow Scan Television). Now, to receive these pictures using a specific method called Digital Radio Mondiale (DRM), you need a special type of receiver. Think of it like needing a specific kind of TV to watch a certain channel. In this case, the right TV is an SSB (Single Sideband) receiver. It’s like the perfect tool to unlock the magic of seeing pictures through your radio!

\subsubsection{Advanced Explanation}
To receive and decode SSTV signals using the Digital Radio Mondiale (DRM) protocol, an SSB (Single Sideband) receiver is required. SSTV signals are typically transmitted in the HF (High Frequency) bands, and SSB is a common modulation technique used in these bands. SSB receivers are designed to demodulate signals where one of the sidebands and the carrier have been suppressed, which is efficient for long-distance communication.

The DRM protocol is a digital broadcasting system that can carry audio, text, and images, including SSTV. SSB receivers are capable of receiving these signals because they can handle the modulation scheme used in DRM transmissions. Other options like CDMA, AREDN, and AM are not suitable for this purpose. CDMA is a digital cellular technology, AREDN is used for high-speed data networks, and AM is an analog modulation technique that does not support the digital requirements of DRM.

In summary, the correct choice is \textbf{D: SSB}, as it is the appropriate receiver technology for decoding SSTV signals using the DRM protocol.

% Diagram Prompt: Generate a diagram showing the process of receiving SSTV signals using an SSB receiver and the DRM protocol.