\subsection{Explore the Magic of Self-Alternating Circuits!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E7A05]
    \textbf{E7A05} Which of the following circuits continuously alternates between two states without an external clock signal?
    \begin{enumerate}[label=\Alph*),noitemsep]
        \item Monostable multivibrator
        \item J-K flip-flop
        \item T flip-flop
        \item \textbf{Astable multivibrator}
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine a light switch that keeps turning on and off by itself without anyone touching it. That's what an astable multivibrator does! It’s like a little machine that keeps flipping between two states, like a light turning on and off, all by itself. The other circuits either need a push (like a clock signal) to change states or only change once and stay that way. But the astable multivibrator is special because it keeps going back and forth without any help!

\subsubsection{Advanced Explanation}
An astable multivibrator is a type of oscillator circuit that generates a continuous square wave without requiring an external clock signal. It operates by using two transistors or operational amplifiers in a feedback loop, where each stage alternately switches the other on and off. The timing of the oscillations is determined by the values of resistors and capacitors in the circuit.

The key characteristic of an astable multivibrator is that it has no stable state; it continuously oscillates between two quasi-stable states. This is in contrast to:
- A \textbf{monostable multivibrator}, which has one stable state and one quasi-stable state, returning to the stable state after a single pulse.
- A \textbf{J-K flip-flop} and \textbf{T flip-flop}, which are bistable devices requiring an external clock signal to change states.

The frequency of oscillation \( f \) for an astable multivibrator can be calculated using the formula:
\[
f = \frac{1}{T}
\]
where \( T \) is the period of oscillation, determined by the RC time constants in the circuit.

Related concepts include:
- \textbf(Feedback loops): Essential for maintaining oscillations.
- \textbf(RC timing circuits): Determine the frequency of oscillation.
- \textbf(Transistor switching): The mechanism by which the circuit alternates between states.

% Prompt for diagram: Generate a diagram showing the basic circuit of an astable multivibrator with two transistors, resistors, and capacitors, illustrating the feedback loop and the output waveform.