\subsection{Exploring the Magic of Truth Tables!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E7A10] What is a truth table?  
    \begin{enumerate}[label=\Alph*),noitemsep]
        \item A list of inputs and corresponding outputs for an op-amp
        \item \textbf{A list of inputs and corresponding outputs for a digital device}
        \item A diagram showing logic states when the digital gate output is true
        \item A table of logic symbols that indicate the logic states of an op-amp
    \end{enumerate}
\end{tcolorbox}

\subsubsection*{Intuitive Explanation}
Imagine you have a magical box that takes in some inputs and gives you an output based on those inputs. A truth table is like a cheat sheet that tells you exactly what the output will be for every possible combination of inputs. For example, if you have a box that adds two numbers, the truth table would show you all the possible sums you can get by putting in different pairs of numbers. In the world of digital devices, like computers, truth tables help us understand how these devices make decisions based on the inputs they receive.

\subsubsection*{Advanced Explanation}
A truth table is a mathematical table used in logic, specifically in Boolean algebra, to represent the output of a digital logic circuit for all possible combinations of input values. Each row of the truth table corresponds to a unique combination of input values, and the output column shows the result of the logical operation performed by the circuit.

For example, consider a simple AND gate with two inputs, \( A \) and \( B \). The truth table for this gate would be:

\[
\begin{array}{|c|c|c|}
\hline
A & B & \text{Output} \\
\hline
0 & 0 & 0 \\
0 & 1 & 0 \\
1 & 0 & 0 \\
1 & 1 & 1 \\
\hline
\end{array}
\]

In this table, the output is 1 only when both \( A \) and \( B \) are 1. This is the fundamental behavior of an AND gate. Truth tables are essential tools in digital logic design, allowing engineers to predict the behavior of complex circuits by breaking them down into simpler components.

% Diagram Prompt: Generate a diagram showing a simple AND gate with its corresponding truth table.