\subsection{Digital Voice Modes}
\label{G8C16}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G8C16]
Which of the following provide digital voice modes?
\begin{enumerate}[label=\Alph*),noitemsep]
    \item WSPR, MFSK16, and EasyPAL
    \item FT8, FT4, and FST4
    \item Winlink, PACTOR II, and PACTOR III
    \item \textbf{DMR, D-STAR, and SystemFusion}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're talking to your friend on a walkie-talkie, but instead of using regular voice, you're using a secret code that only your walkie-talkie can understand. That's what digital voice modes are like! They turn your voice into a digital signal that can be sent over the airwaves. In this question, you're asked to pick which of the options are these special digital voice modes. The correct answer is DMR, D-STAR, and SystemFusion—they're like the superheroes of digital voice communication!

\subsubsection{Advanced Explanation}
Digital voice modes in radio communication involve converting analog voice signals into digital data packets, which are then transmitted over the air. This process typically involves encoding, modulation, and error correction techniques to ensure reliable communication. 

The options provided in the question are:
\begin{itemize}
    \item \textbf{DMR (Digital Mobile Radio)}: A digital radio standard that uses Time Division Multiple Access (TDMA) to allow two voice channels to share the same frequency.
    \item \textbf{D-STAR (Digital Smart Technologies for Amateur Radio)}: A digital voice and data protocol that uses Gaussian Minimum Shift Keying (GMSK) modulation.
    \item \textbf{System Fusion}: A digital mode developed by Yaesu that supports both digital and analog communication, using Continuous 4-level FM (C4FM) modulation.
\end{itemize}

These technologies are designed to provide clear, reliable voice communication with additional features such as text messaging and GPS data transmission. The other options listed (WSPR, MFSK16, EasyPAL, FT8, FT4, FST4, Winlink, PACTOR II, and PACTOR III) are primarily used for data communication rather than voice.

% Diagram prompt: A diagram showing the process of converting analog voice to digital signals and transmitting them via DMR, D-STAR, and SystemFusion would be helpful here.