\subsection{Bandwidth of AM Fast-Scan TV Transmissions}
\label{T8A10}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T8A10]
What is the approximate bandwidth of AM fast-scan TV transmissions?
\begin{enumerate}[label=\Alph*)]
    \item More than 10 MHz
    \item \textbf{About 6 MHz}
    \item About 3 MHz
    \item About 1 MHz
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're watching your favorite TV show. The picture and sound are being sent to your TV through the air, kind of like how you send a text message. But instead of using a phone, the TV station uses a special kind of signal called AM fast-scan TV. This signal needs a certain amount of space to carry all the information for the picture and sound. That space is called bandwidth. For AM fast-scan TV, this space is about 6 MHz. That's like having a 6-lane highway for all the data to travel on!

\subsubsection{Advanced Explanation}
The bandwidth of a signal is the range of frequencies it occupies. For AM fast-scan TV transmissions, the bandwidth is determined by the video and audio components of the signal. The video signal typically requires a bandwidth of about 4.2 MHz, and the audio signal requires an additional 0.5 MHz. Therefore, the total bandwidth is approximately 4.2 MHz + 0.5 MHz = 4.7 MHz. However, to accommodate guard bands and ensure minimal interference, the total bandwidth is rounded up to about 6 MHz.

The formula for calculating the bandwidth \( B \) is:
\[
B = B_{\text{video}} + B_{\text{audio}} + B_{\text{guard}}
\]
where \( B_{\text{video}} \) is the bandwidth of the video signal, \( B_{\text{audio}} \) is the bandwidth of the audio signal, and \( B_{\text{guard}} \) is the bandwidth allocated for guard bands. In this case:
\[
B \approx 4.2 \, \text{MHz} + 0.5 \, \text{MHz} + 1.3 \, \text{MHz} = 6 \, \text{MHz}
\]

This ensures that the signal can carry all the necessary information without significant interference from other signals.

% Prompt for generating a diagram: A diagram showing the frequency spectrum of an AM fast-scan TV signal, with labeled sections for video, audio, and guard bands.