\subsection{Maximum Permissible Exposure Frequencies}
\label{T0C02}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T0C02]
At which of the following frequencies does maximum permissible exposure have the lowest value?
\begin{enumerate}[label=\Alph*)]
    \item 3.5 MHz
    \item \textbf{50 MHz}
    \item 440 MHz
    \item 1296 MHz
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're standing in front of a giant speaker playing music. The lower the frequency of the sound, the less it bothers you, right? Now, think of radio frequencies like different pitches of sound. The lower the frequency, the less energy it carries, and the less it can affect you. So, the frequency with the lowest maximum permissible exposure is like the quietest one in terms of energy. In this case, 50 MHz is the quietest frequency among the options, meaning it has the lowest maximum permissible exposure.

\subsubsection{Advanced Explanation}
Maximum Permissible Exposure (MPE) refers to the maximum level of electromagnetic field strength to which a person can be exposed without harmful effects. The MPE values are frequency-dependent, meaning they vary with the frequency of the electromagnetic radiation. Generally, the MPE decreases as the frequency increases, but there are specific frequency ranges where the MPE is particularly low.

In this question, we are given four frequencies: 3.5 MHz, 50 MHz, 440 MHz, and 1296 MHz. The MPE is lowest at 50 MHz. This is because, in the frequency range around 30 MHz to 300 MHz, the human body is more susceptible to electromagnetic radiation, leading to stricter MPE limits. 

To understand this better, consider the relationship between frequency and energy. The energy \(E\) of a photon is given by the equation:
\[
E = h \cdot f
\]
where \(h\) is Planck's constant (\(6.626 \times 10^{-34} \, \text{Js}\)) and \(f\) is the frequency. However, the MPE is not solely determined by the energy of the photons but also by how the human body interacts with different frequencies. At around 50 MHz, the body's absorption of electromagnetic energy is more efficient, leading to lower MPE values.

% Prompt for generating a diagram: 
% Create a diagram showing the relationship between frequency and Maximum Permissible Exposure (MPE). The x-axis should represent frequency (in MHz), and the y-axis should represent MPE (in W/m²). Highlight the point at 50 MHz to show where the MPE is the lowest.