\subsection{Power Gain Devices}
\label{T6B10}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T6B10]
Which of the following can provide power gain?
\begin{enumerate}[label=\Alph*)]
    \item Transformer
    \item \textbf{Transistor}
    \item Reactor
    \item Resistor
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a tiny whisper, and you want to turn it into a loud shout. You need something that can take that small sound and make it bigger. A transistor is like a magical volume knob for electrical signals. It can take a small signal and make it much stronger, giving you a power boost. Transformers, reactors, and resistors are more like traffic cops—they manage the flow of electricity but don’t make it stronger. So, if you want to crank up the volume, you need a transistor!

\subsubsection{Advanced Explanation}
A transistor is a semiconductor device that can amplify electrical signals, providing power gain. Power gain is the ratio of the output power to the input power, and it is a key feature of active components like transistors. The transistor operates by controlling the flow of current between its terminals (collector, base, and emitter) using a small input signal at the base. This control allows the transistor to amplify the signal, resulting in a higher output power than the input power.

Mathematically, the power gain \( G \) can be expressed as:
\[
G = \frac{P_{\text{out}}}{P_{\text{in}}}
\]
where \( P_{\text{out}} \) is the output power and \( P_{\text{in}} \) is the input power. For a transistor, \( G > 1 \), indicating that it provides power gain.

In contrast, a transformer can change the voltage and current levels but does not provide power gain because the output power is ideally equal to the input power (neglecting losses). Reactors (inductors) and resistors are passive components that do not amplify signals; they either store energy (reactors) or dissipate it as heat (resistors).

% Diagram Prompt: Generate a diagram showing a transistor amplifying a small input signal to a larger output signal.