\subsection{Optimal Power Connection for HF Mobile Installation}
\label{G4E03}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G4E03]
Which of the following direct, fused power connections would be the best for a 100-watt HF mobile installation?
\begin{enumerate}[label=\Alph*)]
    \item \textbf{To the battery using heavy-gauge wire}
    \item To the alternator or generator using heavy-gauge wire
    \item To the battery using insulated heavy duty balanced transmission line
    \item To the alternator or generator using insulated heavy duty balanced transmission line
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine your car is like a giant toy that needs power to run. The battery is like the toy's energy pack, and the alternator is like a little helper that keeps the energy pack charged. Now, if you want to power a small radio in your car, you need to connect it to the energy pack (the battery) directly with a thick, strong wire. This way, the radio gets all the power it needs without any interruptions. Connecting it to the alternator or using a fancy transmission line would be like trying to power your toy with a helper or a complicated cable—it’s just not the best way to go!

\subsubsection{Advanced Explanation}
In a mobile HF (High Frequency) installation, the power supply must be stable and capable of handling the current demands of the transmitter. The battery in a vehicle provides a stable DC voltage source, which is ideal for powering radio equipment. Heavy-gauge wire is necessary to minimize voltage drop and ensure efficient power delivery, especially for a 100-watt transmitter, which can draw significant current.

The alternator or generator, while a source of power, is not as stable as the battery due to fluctuations in engine speed and electrical load. Insulated heavy-duty balanced transmission lines are typically used for RF signals, not for DC power connections, making them unsuitable for this application.

Therefore, the optimal connection is directly to the battery using heavy-gauge wire, ensuring a stable and efficient power supply for the HF mobile installation.

% Diagram prompt: A simple diagram showing a car battery connected to a radio transmitter with heavy-gauge wire, illustrating the direct power connection.