\subsection{Driven Element Length of a Yagi Antenna}
\label{G9C02}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G9C02]
What is the approximate length of the driven element of a Yagi antenna?
\begin{enumerate}[label=\Alph*)]
    \item 1/4 wavelength
    \item \textbf{1/2 wavelength}
    \item 3/4 wavelength
    \item 1 wavelength
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine a Yagi antenna as a team of cheerleaders. The driven element is like the main cheerleader who does most of the work. Just like the main cheerleader stands in the middle of the team, the driven element is usually about half the length of the wave it's cheering for. So, if the wave is doing a big jump, the driven element is right in the middle, ready to catch it!

\subsubsection{Advanced Explanation}
The driven element of a Yagi antenna is typically designed to be resonant at the operating frequency. Resonance occurs when the length of the element is such that it efficiently radiates or receives electromagnetic waves. For a half-wave dipole, the length \( L \) is given by:

\[
L = \frac{\lambda}{2}
\]

where \( \lambda \) is the wavelength of the operating frequency. The wavelength \( \lambda \) can be calculated using the formula:

\[
\lambda = \frac{c}{f}
\]

where \( c \) is the speed of light (\( 3 \times 10^8 \) meters per second) and \( f \) is the frequency in hertz. For example, if the operating frequency is 146 MHz, the wavelength \( \lambda \) is approximately 2.05 meters, making the driven element approximately 1.025 meters long.

The Yagi antenna consists of multiple elements, including the driven element, reflector, and directors. The driven element is the only element that is directly connected to the transmission line and is responsible for the primary radiation or reception of the signal. The other elements help to direct and focus the signal, improving the antenna's gain and directivity.

% Diagram prompt: Generate a diagram showing the structure of a Yagi antenna with labeled elements including the driven element, reflector, and directors.