\subsection{Voltage Gain Delight: What’s in Store for R1 and RF?}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=Multiple Choice Question]
    \textbf{E7G10} What absolute voltage gain can be expected from the circuit in Figure E7-3 when R1 is 1,800 ohms and RF is 68 kilohms?
    \begin{enumerate}[label=\Alph*,noitemsep]
        \item 1
        \item 0.03
        \item \textbf{38}
        \item 76
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a simple machine that takes a small amount of force (voltage) and makes it bigger. In this case, the machine is a circuit with two resistors, R1 and RF. R1 is like the small force you put in, and RF is like the big force you get out. The ratio of RF to R1 tells you how much bigger the output force is compared to the input force. Here, RF is 68,000 ohms and R1 is 1,800 ohms. If you divide 68,000 by 1,800, you get about 38. So, the output force is 38 times bigger than the input force. That’s why the voltage gain is 38.

\subsubsection{Advanced Explanation}
The circuit in question is an inverting operational amplifier (op-amp) configuration. The voltage gain \( A_v \) of an inverting op-amp is given by the formula:

\[
A_v = -\frac{R_F}{R_1}
\]

Where:
- \( R_F \) is the feedback resistor (68 k$\Omega$)
- \( R_1 \) is the input resistor (1.8 k$\Omega$)

Substituting the given values:

\[
A_v = -\frac{68,000}{1,800} \approx -37.78
\]

The negative sign indicates that the output voltage is inverted relative to the input voltage. However, the question asks for the absolute voltage gain, so we take the magnitude:

\[
|A_v| = 37.78 \approx 38
\]

Thus, the absolute voltage gain is 38.

\subsubsection{Related Concepts}
The inverting op-amp configuration is a fundamental circuit in electronics. The gain is determined by the ratio of the feedback resistor \( R_F \) to the input resistor \( R_1 \). This configuration is widely used in signal processing, amplification, and filtering applications. Understanding the relationship between the resistors and the gain is crucial for designing and analyzing such circuits.

% Diagram prompt: Generate a diagram of an inverting operational amplifier circuit with R1 and RF labeled.