\subsection{Sunshine to Power: What Makes Photovoltaic Cells Work?}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=\textbf{E6F01}]
\textbf{What absorbs the energy from light falling on a photovoltaic cell?}
\begin{enumerate}[label=\Alph*.]
    \item Protons
    \item Photons
    \item \textbf{Electrons}
    \item Holes
\end{enumerate}
\end{tcolorbox}

\subsubsection*{Intuitive Explanation}
Imagine a photovoltaic cell as a tiny power plant that turns sunlight into electricity. When sunlight hits the cell, it’s like throwing a ball into a game. The ball (which is the light) gives energy to the players (which are the electrons) in the cell. These electrons get excited and start moving around, creating electricity. So, it’s the electrons that absorb the energy from the light and make the whole process work.

\subsubsection*{Advanced Explanation}
Photovoltaic cells operate based on the principle of the photoelectric effect. When photons (particles of light) with sufficient energy strike the surface of a semiconductor material (typically silicon) in the photovoltaic cell, they transfer their energy to electrons in the valence band of the semiconductor. This energy excites the electrons, causing them to jump to the conduction band, leaving behind holes (positive charge carriers). The movement of these excited electrons and holes creates an electric current. 

Mathematically, the energy of a photon \( E \) is given by:
\[
E = h \nu
\]
where \( h \) is Planck's constant and \( \nu \) is the frequency of the light. For an electron to be excited from the valence band to the conduction band, the photon energy must be greater than or equal to the bandgap energy \( E_g \) of the semiconductor:
\[
E \geq E_g
\]
Once the electrons are in the conduction band, they can move freely, generating an electric current when an external circuit is connected.

The correct answer is \textbf{C: Electrons}, as they are the particles that absorb the energy from the photons and generate the electric current.

% Prompt for diagram: A diagram showing the process of photon absorption, electron excitation, and current generation in a photovoltaic cell would be helpful here.