\subsection{Opposition to AC Flow in a Capacitor}
\label{G5A04}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G5A04]
Which of the following is opposition to the flow of alternating current in a capacitor?
\begin{enumerate}[label=\Alph*,noitemsep]
    \item Conductance
    \item Reluctance
    \item \textbf{Reactance}
    \item Admittance
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're trying to push water through a sponge. The sponge doesn't let the water flow easily, right? It's like it's opposing the flow of water. In the world of electricity, a capacitor is like that sponge, but for alternating current (AC). The capacitor doesn't let the AC flow smoothly; it resists it. This resistance is called reactance. So, when you hear reactance, think of the capacitor being a bit stubborn and not letting the AC flow easily.

\subsubsection{Advanced Explanation}
In electrical circuits, the opposition to the flow of alternating current (AC) in a capacitor is known as capacitive reactance, denoted by \( X_C \). The formula for capacitive reactance is given by:

\[
X_C = \frac{1}{2\pi f C}
\]

where:
\begin{itemize}
    \item \( X_C \) is the capacitive reactance in ohms ($\Omega$),
    \item \( f \) is the frequency of the AC signal in hertz (Hz),
    \item \( C \) is the capacitance in farads (F).
\end{itemize}

Capacitive reactance decreases with increasing frequency and capacitance. This means that at higher frequencies or with larger capacitors, the opposition to the AC flow is reduced. Reactance is a purely imaginary quantity in the context of complex impedance, which combines resistance and reactance to describe the total opposition to AC in a circuit.

Conductance (A) is the reciprocal of resistance and measures how easily current flows through a conductor. Reluctance (B) is a concept in magnetic circuits, analogous to resistance in electrical circuits, and is not related to capacitors. Admittance (D) is the reciprocal of impedance and measures how easily AC flows through a circuit, but it is not specifically the opposition to AC flow in a capacitor.

% Diagram prompt: A simple circuit diagram showing a capacitor connected to an AC source, with labels for the capacitive reactance \( X_C \), frequency \( f \), and capacitance \( C \).