\subsection{Unlocking the 60-Meter Bandwidth Wonders!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E1C01] What is the maximum bandwidth for a data emission on 60 meters?  
    \begin{enumerate}[label=\Alph*)]
        \item 60 Hz
        \item 170 Hz
        \item 1.5 kHz
        \item \textbf{2.8 kHz}
    \end{enumerate}
\end{tcolorbox}

\subsubsection*{Intuitive Explanation}
Imagine you have a water pipe, and the amount of water that can flow through it depends on how wide the pipe is. In radio terms, the pipe is the bandwidth, and the water is the data. The 60-meter band is like a specific type of pipe that can only handle a certain amount of data at once. The maximum bandwidth for data on the 60-meter band is 2.8 kHz, which means it can handle a lot more data than the other options listed.

\subsubsection*{Advanced Explanation}
The 60-meter band is a part of the radio spectrum allocated for amateur radio use. The bandwidth of a signal is the range of frequencies it occupies. For data emissions on the 60-meter band, the maximum allowed bandwidth is 2.8 kHz. This is determined by regulatory bodies to ensure that different users can share the spectrum without interfering with each other.

To understand why 2.8 kHz is the correct answer, consider the following:

1. **Regulatory Limits**: The International Telecommunication Union (ITU) and national regulatory agencies set specific limits on bandwidth to prevent interference. For the 60-meter band, this limit is 2.8 kHz.

2. **Frequency Range**: The 60-meter band spans from 5.3305 MHz to 5.4035 MHz. The bandwidth of a signal must fit within this range, and 2.8 kHz is the maximum allowed.

3. **Signal Integrity**: A wider bandwidth allows for more data to be transmitted, but it also requires more power and can cause interference. The 2.8 kHz limit is a balance between data capacity and interference management.

In summary, the maximum bandwidth for a data emission on the 60-meter band is 2.8 kHz, as it is the regulatory limit that ensures efficient and interference-free communication.

% [Prompt for diagram: A diagram showing the frequency spectrum of the 60-meter band with the 2.8 kHz bandwidth highlighted would be helpful here.]