\subsection{Delightful Dilemmas: When Can Stations Share Third-Party Chats?}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E1C05] Under what situation may a station transmit third party communications while being automatically controlled?
    \begin{enumerate}[label=\Alph*]
        \item Never
        \item \textbf{Only when transmitting RTTY or data emissions}
        \item Only when transmitting SSB or CW
        \item On any mode approved by the National Telecommunication and Information Administration
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a robot that can send messages for you. Normally, this robot isn't allowed to send messages from other people (third-party communications). However, there's a special rule: if the robot is sending messages using certain types of signals, like RTTY or data emissions, then it's okay for it to send messages from other people. Think of it like a special permission slip that allows the robot to do this specific job.

\subsubsection{Advanced Explanation}
In the context of radio communications, automatic control refers to a station that operates without a human operator present at all times. The Federal Communications Commission (FCC) has specific regulations regarding third-party communications, which are messages sent on behalf of someone else. According to FCC rules, a station under automatic control is permitted to transmit third-party communications only when using RTTY (Radio Teletype) or data emissions. This is because these modes are considered more controlled and less prone to misuse compared to voice modes like SSB (Single Side Band) or CW (Continuous Wave).

The rationale behind this regulation is to ensure that third-party communications are transmitted in a manner that minimizes the risk of unauthorized or inappropriate use. RTTY and data emissions are typically used for specific, well-defined purposes, making them more suitable for third-party communications under automatic control.

% Diagram Prompt: Generate a diagram showing the flow of third-party communications under automatic control, highlighting the allowed modes (RTTY and data emissions) and the restrictions on other modes (SSB and CW).