\subsection{Happy Hints for 630 and 2200 Meter Band Transmissions!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E1C07] What notifications must be given before transmitting on the 630- or 2200-meter bands?
    \begin{enumerate}[label=\Alph*]
        \item A special endorsement must be requested from the FCC
        \item An environmental impact statement must be filed with the Department of the Interior
        \item Operators must inform the FAA of their intent to operate, giving their call sign and distance to the nearest runway
        \item \textbf{Operators must inform the Utilities Technology Council (UTC) of their call sign and coordinates of the station}
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you want to use a special radio frequency to talk to people far away. Before you start, you need to tell a special group called the Utilities Technology Council (UTC) who you are and where you are. This is like telling your teacher where you are sitting in class so they know who is talking. This helps make sure that your radio signals don’t interfere with important things like power lines or other utilities.

\subsubsection{Advanced Explanation}
The 630- and 2200-meter bands are part of the Low Frequency (LF) and Medium Frequency (MF) spectrum, respectively. These bands are shared with other services, including power utilities, which use them for power line communication and other critical infrastructure. To prevent interference, the Federal Communications Commission (FCC) requires amateur radio operators to notify the Utilities Technology Council (UTC) before transmitting on these bands. The notification must include the operator's call sign and the geographic coordinates of the station. This ensures that the UTC can coordinate with amateur operators to avoid conflicts with utility operations.

The correct answer is \textbf{D}, as it aligns with the regulatory requirements set forth by the FCC for amateur radio operations on these bands.

% [Prompt for diagram: A diagram showing the frequency spectrum with the 630- and 2200-meter bands highlighted, along with a flowchart of the notification process to the UTC.]