\subsection{SWR Reading of 4:1}
\label{T7C06}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T7C06]
What does an SWR reading of 4:1 indicate?
\begin{enumerate}[label=\Alph*)]
    \item Loss of -4 dB
    \item Good impedance match
    \item Gain of +4 dB
    \item \textbf{Impedance mismatch}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're trying to pour water from a big jug into a small cup. If the jug is too big or the cup is too small, you'll end up spilling a lot of water. This is kind of like what happens with an SWR (Standing Wave Ratio) reading of 4:1. It tells us that the radio waves are not flowing smoothly from the transmitter to the antenna because there's a mismatch in their sizes (or in technical terms, their impedances). So, instead of all the energy going out as a nice signal, some of it bounces back, causing a mess. That's why an SWR of 4:1 means there's an impedance mismatch.

\subsubsection{Advanced Explanation}
The Standing Wave Ratio (SWR) is a measure of how well the impedance of the transmitter matches the impedance of the antenna. When the impedances match perfectly, the SWR is 1:1, indicating that all the power is transferred from the transmitter to the antenna without any reflection. However, when there is a mismatch, some of the power is reflected back towards the transmitter, creating standing waves.

The SWR is calculated as:
\[
\text{SWR} = \frac{V_{\text{max}}}{V_{\text{min}}}
\]
where \(V_{\text{max}}\) is the maximum voltage of the standing wave and \(V_{\text{min}}\) is the minimum voltage.

An SWR of 4:1 indicates a significant impedance mismatch. This means that the impedance of the antenna is either much higher or much lower than the impedance of the transmission line. As a result, a substantial portion of the transmitted power is reflected back, reducing the efficiency of the transmission.

In practical terms, an SWR of 4:1 suggests that the system is not operating optimally, and adjustments may be needed to improve the impedance match, such as using an antenna tuner or adjusting the antenna length.

% Diagram prompt: Generate a diagram showing the relationship between SWR, impedance mismatch, and reflected power.