\subsection{UV Resistance in Coaxial Cable Jackets}
\label{T7C10}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T7C10]
Why should the outer jacket of coaxial cable be resistant to ultraviolet light?
\begin{enumerate}[label=\Alph*)]
    \item Ultraviolet resistant jackets prevent harmonic radiation
    \item Ultraviolet light can increase losses in the cable’s jacket
    \item Ultraviolet and RF signals can mix, causing interference
    \item \textbf{Ultraviolet light can damage the jacket and allow water to enter the cable}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine your coaxial cable is like a superhero’s cape. If the cape gets torn by the sun’s UV rays, water can sneak in and ruin the superhero’s day (or in this case, the cable’s performance). So, the outer jacket needs to be UV-resistant to keep the cable safe and dry, just like a strong, unbreakable cape!

\subsubsection{Advanced Explanation}
The outer jacket of a coaxial cable serves as a protective barrier against environmental factors, including ultraviolet (UV) radiation. UV light has a wavelength range of 10 nm to 400 nm and is known to cause photodegradation in many materials. When the jacket material is exposed to UV light, it can undergo a process called photo-oxidation, which breaks down the polymer chains in the material. This degradation can lead to cracks and brittleness in the jacket, compromising its integrity.

Once the jacket is compromised, moisture can penetrate the cable. Water ingress can significantly affect the cable’s performance by increasing the dielectric loss and potentially causing short circuits. The dielectric loss \( \alpha_d \) can be calculated using the formula:

\[
\alpha_d = \frac{2\pi f \epsilon''}{c \sqrt{\epsilon'}}
\]

where \( f \) is the frequency, \( \epsilon'' \) is the imaginary part of the complex permittivity, \( c \) is the speed of light, and \( \epsilon' \) is the real part of the complex permittivity. Water has a high dielectric constant, which increases \( \epsilon'' \), leading to higher losses.

Therefore, a UV-resistant jacket is crucial to maintain the cable’s performance and longevity by preventing physical damage and subsequent water ingress.

% Prompt for diagram: A diagram showing the structure of a coaxial cable with labels for the outer jacket, inner conductor, dielectric, and shield, highlighting the importance of the UV-resistant outer jacket.