\subsection{Administration of Technician Class License Examination}
\label{G1D04}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G1D04]
Who must observe the administration of a Technician class license examination?
\begin{enumerate}[label=\Alph*,noitemsep]
    \item \textbf{At least three Volunteer Examiners of General class or higher}
    \item At least two Volunteer Examiners of General class or higher
    \item At least two Volunteer Examiners of Technician class or higher
    \item At least three Volunteer Examiners of Technician class
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're taking a big test, like the one you take to get your driver's license. Now, think of the people who are watching over you while you take that test. They’re like the referees in a game, making sure everything is fair and follows the rules. For a Technician class license exam, there needs to be at least three of these referees, and they have to be really good at what they do—like having a higher level of license themselves. This way, they can make sure everything is done correctly and fairly.

\subsubsection{Advanced Explanation}
In the context of amateur radio licensing, the administration of examinations is a critical process to ensure that candidates meet the necessary standards. The Federal Communications Commission (FCC) mandates that the administration of a Technician class license examination must be observed by at least three Volunteer Examiners (VEs). These VEs must hold a General class license or higher, ensuring they possess the requisite knowledge and experience to oversee the examination process.

The rationale behind requiring three VEs is to maintain the integrity and fairness of the examination. Multiple observers reduce the likelihood of errors or biases, and the requirement for General class or higher ensures that the VEs have a deeper understanding of the material and the examination process. This structure is designed to uphold the standards of the amateur radio community and ensure that all licensees are competent and knowledgeable.

% Prompt for diagram: A diagram showing the setup of a Technician class license examination room with three Volunteer Examiners observing the candidates could be helpful here.