\subsection{G1D03: Technician Class Operator Band Segments with General Class CSCE}
\label{G1D03}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G1D03]
On which of the following band segments may you operate if you are a Technician class operator and have an unexpired Certificate of Successful Completion of Examination (CSCE) for General class privileges?
\begin{enumerate}[label=\Alph*,noitemsep]
    \item Only the Technician band segments until your upgrade is posted in the FCC database
    \item Only on the Technician band segments until you have a receipt for the FCC application fee payment
    \item \textbf{On any General or Technician class band segment}
    \item On any General or Technician class band segment except 30 meters and 60 meters
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you just passed a test that lets you drive a bigger, cooler car, but you’re still waiting for the official license to arrive. Even though you don’t have the official license yet, you’ve got a special paper that says, “Hey, I passed the test!” This paper lets you drive the bigger car right away. Similarly, if you’re a Technician class ham radio operator and you’ve passed the General class test, you can operate on the General class band segments even before the FCC officially updates your license. So, you’re not stuck with just the Technician bands—you get to explore more frequencies!

\subsubsection{Advanced Explanation}
The Federal Communications Commission (FCC) allows Technician class operators who have successfully passed the General class examination to operate on General class band segments immediately, provided they possess an unexpired Certificate of Successful Completion of Examination (CSCE). This is outlined in FCC rules, which state that the CSCE grants temporary operating privileges equivalent to the General class license until the upgrade is officially processed and reflected in the FCC database.

The correct answer, \textbf{C}, indicates that the operator can operate on any General or Technician class band segment. This includes all frequencies allocated to both classes, except for specific restrictions like the 30 meters and 60 meters bands, which are not included in this temporary privilege. This rule ensures that operators can immediately utilize their newly acquired knowledge and skills without unnecessary delays.

% Prompt for diagram: A diagram showing the frequency bands allocated to Technician and General class operators, highlighting the overlap and the temporary privileges granted by the CSCE.