\subsection{G1D01: Partial Credit for Expired Amateur Radio License}
\label{G1D01}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G1D01]
Who may receive partial credit for the elements represented by an expired amateur radio license?
\begin{enumerate}[label=\Alph*,noitemsep]
    \item \textbf{Any person who can demonstrate that they once held an FCC-issued General, Advanced, or Amateur Extra class license that was not revoked by the FCC}
    \item Anyone who held an FCC-issued amateur radio license that expired not less than 5 and not more than 15 years ago
    \item Any person who previously held an amateur license issued by another country, but only if that country has a current reciprocal licensing agreement with the FCC
    \item Only persons who once held an FCC issued Novice, Technician, or Technician Plus license
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you once had a special ticket (like a license) to play with radios, but it expired. Now, you want to get back into the radio game, but you don't want to start from scratch. The FCC (the people who give out these tickets) says, Hey, if you can prove you had a General, Advanced, or Amateur Extra ticket before, and we didn't take it away, we'll give you some credit! So, you don't have to do everything over again. It's like getting a head start in a race because you've already run part of it before.

\subsubsection{Advanced Explanation}
The Federal Communications Commission (FCC) allows individuals who previously held certain classes of amateur radio licenses to receive partial credit for the elements of the license examination. Specifically, if a person can demonstrate that they once held a General, Advanced, or Amateur Extra class license that was not revoked by the FCC, they are eligible for this credit. This policy is designed to facilitate the re-entry of experienced operators into the amateur radio community without requiring them to retake the entire examination process.

The eligibility criteria are as follows:
\begin{itemize}
    \item The license must have been issued by the FCC.
    \item The license must not have been revoked.
    \item The license must have been one of the higher-tier classes (General, Advanced, or Amateur Extra).
\end{itemize}

This policy recognizes the prior knowledge and experience of the licensee, thereby streamlining the process of re-licensing. It is important to note that this provision does not apply to individuals who held Novice, Technician, or Technician Plus licenses, as these are considered entry-level licenses with fewer privileges.

% Diagram prompt: A flowchart showing the process of receiving partial credit for an expired amateur radio license, including the eligibility criteria and the steps involved.