\subsection{Obtaining a New General Class License After Expiration}
\label{G1D11}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G1D11]
What action is required to obtain a new General class license after a previously held license has expired and the two-year grace period has passed?
\begin{enumerate}[label=\Alph*),noitemsep]
    \item They must have a letter from the FCC showing they once held an amateur or commercial license
    \item There are no requirements other than being able to show a copy of the expired license
    \item Contact the FCC to have the license reinstated
    \item \textbf{The applicant must show proof of the appropriate expired license grant and pass the current Element 2 exam}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine your favorite video game has a special pass that lets you play all the cool levels. But if you don't use it for a long time, it expires. Now, if you want to get back into the game, you can't just show your old pass and expect to jump right in. You need to prove you had the pass before and also pass a quick test to make sure you still know how to play. That's exactly what happens with your General class license. After it expires and the grace period is over, you need to show you had it before and pass a new test to get it back.

\subsubsection{Advanced Explanation}
When a General class amateur radio license expires and the two-year grace period has passed, the licensee must follow specific procedures to regain their license. According to FCC regulations, the applicant must provide proof of the expired license grant. This proof typically includes documentation such as a copy of the expired license or other official records. Additionally, the applicant must pass the current Element 2 examination, which covers the basic operating practices and regulations for amateur radio operators. This ensures that the applicant is up-to-date with the latest rules and practices in the field. The combination of proof of prior licensure and successful completion of the exam reinstates the individual's eligibility for a General class license.

% Prompt for diagram: A flowchart showing the steps to regain a General class license after expiration and the two-year grace period.