\subsection{Total Resistance of Parallel Resistors}
\label{G5C03}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G5C03]
What is the total resistance of a 10-, a 20-, and a 50-ohm resistor connected in parallel?
\begin{enumerate}[label=\Alph*,noitemsep]
    \item \textbf{5.9 ohms}
    \item 0.17 ohms
    \item 17 ohms
    \item 80 ohms
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have three different-sized pipes connected side by side, and water is flowing through them. The wider the pipe, the easier it is for water to flow. Now, think of the resistors as these pipes. When they are connected in parallel, it's like having multiple paths for the water (or electricity) to flow. The more paths you have, the easier it is for the water to get through. So, the total resistance is less than the smallest individual resistance. In this case, the total resistance is 5.9 ohms, which is less than the smallest resistor (10 ohms).

\subsubsection{Advanced Explanation}
When resistors are connected in parallel, the total resistance \( R_{\text{total}} \) is given by the reciprocal of the sum of the reciprocals of each individual resistance. Mathematically, this is expressed as:

\[
\frac{1}{R_{\text{total}}} = \frac{1}{R_1} + \frac{1}{R_2} + \frac{1}{R_3}
\]

Given the resistances \( R_1 = 10 \, \Omega \), \( R_2 = 20 \, \Omega \), and \( R_3 = 50 \, \Omega \), we can calculate the total resistance as follows:

\[
\frac{1}{R_{\text{total}}} = \frac{1}{10} + \frac{1}{20} + \frac{1}{50}
\]

First, find a common denominator for the fractions, which is 100:

\[
\frac{1}{R_{\text{total}}} = \frac{10}{100} + \frac{5}{100} + \frac{2}{100} = \frac{17}{100}
\]

Now, take the reciprocal to find \( R_{\text{total}} \):

\[
R_{\text{total}} = \frac{100}{17} \approx 5.9 \, \Omega
\]

Thus, the total resistance of the parallel combination is approximately 5.9 ohms.

% Diagram prompt: A diagram showing three resistors connected in parallel with labeled resistances (10 ohms, 20 ohms, and 50 ohms) and the total resistance (5.9 ohms) would be helpful for visualization.