\subsection{Finding the Heart of the Folded Dipole!}
\label{sec:E9C07}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=\textbf{Question E9C07}]
\textbf{What is the approximate feed point impedance at the center of a two-wire half-wave folded dipole antenna?}
\begin{enumerate}[label=\Alph*,noitemsep]
    \item \textbf{300 ohms}
    \item 72 ohms
    \item 50 ohms
    \item 450 ohms
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a folded dipole antenna like a big, stretched-out paperclip. When you feed it with radio waves, it’s like giving it a little shake. Now, the question is: how hard is it to shake this paperclip? The answer is about 300 ohms. Think of it like trying to push a shopping cart with a certain amount of resistance. In this case, the folded dipole has a resistance of 300 ohms at its center, making it a bit harder to push than a regular dipole antenna, which has a lower resistance of 72 ohms. So, the folded dipole is like a shopping cart with a bit more weight in it!

\subsubsection{Advanced Explanation}
The feed point impedance of a two-wire half-wave folded dipole antenna is approximately four times that of a standard half-wave dipole antenna. A standard half-wave dipole antenna has a feed point impedance of about 72 ohms. Therefore, the impedance of the folded dipole can be calculated as follows:

\[
Z_{\text{folded dipole}} = 4 \times Z_{\text{dipole}} = 4 \times 72\,\Omega = 288\,\Omega
\]

Rounding to the nearest standard value, the feed point impedance is approximately 300 ohms. This increase in impedance is due to the folded structure, which effectively doubles the current at the feed point, thereby increasing the impedance by a factor of four.

The folded dipole antenna is often used in applications where a higher impedance is desirable, such as in matching to certain types of transmission lines or in reducing losses in the feed line. The design also provides a broader bandwidth compared to a standard dipole antenna.

% Prompt for diagram: A diagram showing a two-wire half-wave folded dipole antenna with the feed point at the center, labeled with the impedance value of 300 ohms.