\subsection{Key Signage for Telecommand Stations!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E1D05] What must be posted at the location of a station being operated by telecommand on or within 50 kilometers of the Earth’s surface?
    \begin{enumerate}[label=\Alph*,noitemsep]
        \item A photocopy of the station license
        \item A label with the name, address, and telephone number of the station licensee
        \item A label with the name, address, and telephone number of the control operator
        \item \textbf{All these choices are correct}
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a remote-controlled toy car. If you were to leave it somewhere, you’d want to make sure that anyone who finds it knows who it belongs to and how to contact you. Similarly, when operating a radio station by telecommand (which is like remote control for radios), you need to post certain information at the station’s location. This includes a copy of the station’s license, the name and contact details of the person who owns the station, and the person who is controlling it. This way, if someone has questions or concerns, they know who to contact.

\subsubsection{Advanced Explanation}
When operating a station by telecommand, regulatory requirements mandate that specific documentation and identification be posted at the station’s physical location. This ensures transparency and accountability in the operation of the station. The required postings include:

1. \textbf{A photocopy of the station license}: This serves as proof that the station is legally authorized to operate.
2. \textbf{A label with the name, address, and telephone number of the station licensee}: This identifies the individual or entity responsible for the station.
3. \textbf{A label with the name, address, and telephone number of the control operator}: This identifies the person who is currently operating the station.

These requirements are particularly important for stations operating within 50 kilometers of the Earth’s surface, as they are more likely to be accessible to the public or regulatory authorities. The correct answer is \textbf{D}, as all the listed items must be posted.

% Diagram prompt: A diagram showing a telecommand station with labels indicating the required postings (station license, licensee information, and control operator information) could help visualize the setup.