\subsection{Balloon-Borne Telemetry: What's Essential for Identification?}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E1D04]
\textbf{E1D04} Which of the following is required in the identification transmissions from a balloon-borne telemetry station?
\begin{enumerate}[label=\Alph*,noitemsep]
    \item \textbf{Call sign}
    \item The output power of the balloon transmitter
    \item The station's six-character Maidenhead grid locator
    \item All these choices are correct
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a balloon floating high in the sky, and it’s sending information back to the ground. To make sure everyone knows who is sending this information, the balloon needs to say its name, just like when you introduce yourself to someone new. In the world of radio, this name is called a call sign. It’s like a special nickname that helps people recognize who is talking. The other options, like how strong the signal is or where the balloon is located, are important too, but they aren’t the main thing needed to identify the balloon.

\subsubsection{Advanced Explanation}
In radio communications, particularly in telemetry systems where data is transmitted from a balloon to a ground station, identification is crucial for regulatory compliance and operational clarity. The call sign is a unique identifier assigned by the licensing authority, which in this case would be the Federal Communications Commission (FCC) in the United States. This call sign must be included in the transmissions to ensure that the source of the telemetry data is clearly identifiable.

The output power of the transmitter and the Maidenhead grid locator, while useful for technical and locational purposes, are not mandatory for identification. The output power helps in understanding the signal strength and range, and the grid locator provides geographical coordinates, but neither is required for the basic identification of the station.

Therefore, the correct answer is \textbf{A: Call sign}, as it is the only element explicitly required for identification in such transmissions.

% Prompt for diagram: A diagram showing a balloon-borne telemetry station transmitting data to a ground station, with the call sign prominently displayed in the transmission.