\subsection{Power Smarts: Discover the Lowest Consumption Logic Family!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=Multiple Choice Question]
\textbf{E6C05} Which of the following digital logic families has the lowest power consumption?

\begin{enumerate}[label=\Alph*)]
    \item Schottky TTL
    \item ECL
    \item NMOS
    \item \textbf{CMOS}
\end{enumerate}
\end{tcolorbox}

\subsubsection*{Intuitive Explanation}
Imagine you have different types of light bulbs, and you want to find out which one uses the least electricity. In the world of digital logic families, CMOS is like the energy-efficient LED bulb. It uses very little power compared to other types like Schottky TTL, ECL, and NMOS, which are more like incandescent bulbs. CMOS is designed to be super efficient, making it the best choice when you want to save power.

\subsubsection*{Advanced Explanation}
In digital electronics, power consumption is a critical factor, especially in battery-operated devices. CMOS (Complementary Metal-Oxide-Semiconductor) technology is known for its low power consumption due to its unique design. Unlike other logic families, CMOS only consumes significant power during the switching of states (from 0 to 1 or 1 to 0). In a static state (when the output is not changing), CMOS draws almost no current, which is why it is highly efficient.

To understand why CMOS is more efficient, consider the following:

1. \textbf(Schottky TTL (Transistor-Transistor Logic)): This family uses bipolar transistors that draw current continuously, leading to higher power consumption.
2. \textbf(ECL (Emitter-Coupled Logic)): ECL is very fast but consumes a lot of power because it uses current steering logic, which requires constant current flow.
3. \textbf(NMOS (N-type Metal-Oxide-Semiconductor)): NMOS logic uses only N-type transistors, which draw more current than CMOS because they do not have the complementary P-type transistors to balance the current flow.

CMOS, on the other hand, uses both N-type and P-type transistors in a complementary fashion. When one transistor is on, the other is off, minimizing the current flow and thus the power consumption. This makes CMOS the most power-efficient digital logic family.

% Diagram Prompt: Generate a diagram comparing the power consumption of different digital logic families (Schottky TTL, ECL, NMOS, CMOS) to visually illustrate the differences.