\subsection{Determining with a Directional Wattmeter}
\label{G4B10}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G4B10]
Which of the following can be determined with a directional wattmeter?
\begin{enumerate}[label=\Alph*.]
    \item \textbf{Standing wave ratio}
    \item Antenna front-to-back ratio
    \item RF interference
    \item Radio wave propagation
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a magical meter that can tell you how well your radio antenna is working. This meter, called a directional wattmeter, is like a detective that investigates the energy flow in your antenna system. One of the cool things it can figure out is the standing wave ratio (SWR). Think of SWR as a measure of how smoothly the radio waves are traveling along your antenna. If the SWR is high, it's like there's a traffic jam on the antenna, and the waves are bouncing back and forth instead of going out smoothly. The directional wattmeter helps you spot this traffic jam so you can fix it and get your radio waves moving freely again!

\subsubsection{Advanced Explanation}
A directional wattmeter is an instrument used to measure the power flow in a transmission line, typically in radio frequency (RF) systems. It can determine the standing wave ratio (SWR), which is a measure of the impedance matching between the transmission line and the antenna. The SWR is calculated using the formula:

\[
\text{SWR} = \frac{1 + |\Gamma|}{1 - |\Gamma|}
\]

where \(\Gamma\) is the reflection coefficient, which is the ratio of the reflected wave amplitude to the incident wave amplitude. A perfect match (no reflection) results in an SWR of 1, while higher values indicate increasing mismatch and potential signal loss.

The directional wattmeter measures both forward and reflected power, allowing the calculation of SWR. It does not directly measure the antenna front-to-back ratio, RF interference, or radio wave propagation, which require different measurement techniques and instruments.

% Diagram prompt: Generate a diagram showing a directional wattmeter connected to a transmission line, with arrows indicating forward and reflected power.