\subsection{Which HF Bands Have Segments Exclusively Allocated to Amateur Extra Licensees?}
\label{G1A08}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G1A08]
Which HF bands have segments exclusively allocated to Amateur Extra licensees?
\begin{enumerate}[label=\Alph*),noitemsep]
    \item All HF bands
    \item \textbf{80 meters, 40 meters, 20 meters, and 15 meters}
    \item All HF bands except 160 meters and 10 meters
    \item 60 meters, 30 meters, 17 meters, and 12 meters
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you’re at a big party, and there’s a special VIP section where only the coolest people can hang out. In the world of ham radio, the Amateur Extra license holders are like those VIPs. They get access to special segments of certain HF bands—specifically, 80 meters, 40 meters, 20 meters, and 15 meters. These segments are like their exclusive clubhouse where they can communicate without interference from other license classes. So, if you want to join the VIP club, you’ll need to study hard and get that Amateur Extra license!

\subsubsection{Advanced Explanation}
The High Frequency (HF) bands are divided into segments, and different segments are allocated to different license classes. The Amateur Extra license, which is the highest class of amateur radio license in the United States, grants exclusive access to certain segments within the 80 meters (3.5-4.0 MHz), 40 meters (7.0-7.3 MHz), 20 meters (14.0-14.35 MHz), and 15 meters (21.0-21.45 MHz) bands. These segments are reserved for Amateur Extra licensees to ensure they have access to clear communication channels without interference from other license classes.

The allocation of these segments is governed by the Federal Communications Commission (FCC) in the United States. The rationale behind this allocation is to provide advanced operators with more bandwidth and flexibility for experimentation and communication. The Amateur Extra license requires a deeper understanding of radio theory and regulations, which justifies the exclusive access to these segments.

% Prompt for generating a diagram: A diagram showing the HF band allocations with highlighted segments for Amateur Extra licensees would be helpful here.