\subsection{Prohibited Frequencies for General Class Licensees}\label{G1A05}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G1A05]
On which of the following frequencies are General class licensees prohibited from operating as control operator?
\begin{enumerate}[label=\Alph*,noitemsep]
    \item \textbf{7.125 MHz to 7.175 MHz}
    \item 28.000 MHz to 28.025 MHz
    \item 21.275 MHz to 21.300 MHz
    \item All of the above
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're at a big party with different rooms, and each room has its own rules. The General class licensees are like guests who can go to most rooms, but there's one room they're not allowed to enter. That room is the frequency range from 7.125 MHz to 7.175 MHz. So, even though they can go to other rooms (frequencies), they have to stay out of this specific one. It's like being told, You can have fun everywhere except the kitchen!

\subsubsection{Advanced Explanation}
In the United States, the Federal Communications Commission (FCC) regulates the use of radio frequencies. The General class licensees are granted privileges to operate on a wide range of frequencies, but there are specific bands where they are restricted. The frequency range from 7.125 MHz to 7.175 MHz falls within the 40-meter band, which is primarily allocated for Advanced and Extra class licensees. This restriction ensures that higher-class licensees have exclusive access to certain bands, reducing congestion and interference.

The 40-meter band is particularly important for long-distance communication, and the FCC has designated this segment for more experienced operators. The General class licensees are allowed to operate on other segments of the 40-meter band, but not within the 7.125 MHz to 7.175 MHz range. This allocation is part of the broader regulatory framework that balances the needs of different license classes and ensures efficient use of the radio spectrum.

% Diagram Prompt: Generate a diagram showing the frequency allocations for different license classes, highlighting the prohibited range for General class licensees.