\subsection{Advantage of Low Internal Resistance Batteries}
\label{G6A02}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G6A02]
What is an advantage of batteries with low internal resistance?
\begin{enumerate}[label=\Alph*,noitemsep]
    \item Long life
    \item \textbf{High discharge current}
    \item High voltage
    \item Rapid recharge
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a water hose. If the hose is wide and smooth, water can flow through it really fast, right? Now, if the hose is narrow and has a lot of twists and turns, the water flow slows down. Batteries with low internal resistance are like the wide, smooth hose. They let electricity flow out really fast, which means they can power things that need a lot of energy quickly, like a toy car or a flashlight. So, the advantage is that they can give a high discharge current, making them super useful for power-hungry devices!

\subsubsection{Advanced Explanation}
Internal resistance in a battery, denoted as \( r \), is the opposition to the flow of current within the battery itself. According to Ohm's Law, the voltage \( V \) across a battery is given by:
\[
V = E - Ir
\]
where \( E \) is the electromotive force (EMF) of the battery, and \( I \) is the current flowing through the circuit. When the internal resistance \( r \) is low, the voltage drop \( Ir \) across the internal resistance is minimized. This allows the battery to deliver a higher current \( I \) to the external circuit without significant loss of voltage.

The power \( P \) delivered to the external load \( R \) is:
\[
P = I^2 R
\]
Since \( I \) is higher when \( r \) is low, the power delivered to the load is also higher. This is particularly advantageous in applications requiring high discharge currents, such as in electric vehicles or high-performance electronics.

In summary, batteries with low internal resistance can deliver high discharge currents efficiently, making them ideal for applications that demand significant power output.

% Diagram prompt: Generate a diagram showing a battery with low internal resistance connected to a load, illustrating the flow of current and the minimal voltage drop across the internal resistance.