\subsection{Mixing It Up: Key Frequencies Revealed!}
\label{sec:E7E08}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=\textbf{E7E08}]
\textbf{What are the principal frequencies that appear at the output of a mixer?}
\begin{enumerate}[label=\Alph*)]
    \item Two and four times the input frequency
    \item The square root of the product of input frequencies
    \item \textbf{The two input frequencies along with their sum and difference frequencies}
    \item 1.414 and 0.707 times the input frequency
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have two different musical notes playing at the same time. When you mix these notes together, you don't just hear the original notes, but also new notes that are the result of adding and subtracting the frequencies of the original notes. This is similar to what happens in a mixer. The mixer takes two input frequencies and produces not only the original frequencies but also their sum and difference. This is why the correct answer is that the output includes the two input frequencies along with their sum and difference frequencies.

\subsubsection{Advanced Explanation}
In radio technology, a mixer is a nonlinear device that combines two input signals to produce new frequencies. Mathematically, if the two input frequencies are \( f_1 \) and \( f_2 \), the output of the mixer will include the following principal frequencies:

\[
f_{\text{output}} = \{ f_1, f_2, f_1 + f_2, |f_1 - f_2| \}
\]

This phenomenon is a result of the trigonometric identity for the product of two sine waves:

\[
\sin(A) \cdot \sin(B) = \frac{1}{2} [\cos(A - B) - \cos(A + B)]
\]

When two signals with frequencies \( f_1 \) and \( f_2 \) are mixed, the output will contain components at \( f_1 \), \( f_2 \), \( f_1 + f_2 \), and \( |f_1 - f_2| \). This is why the correct answer is that the output includes the two input frequencies along with their sum and difference frequencies.

% Prompt for generating a diagram:
% Diagram showing the input frequencies \( f_1 \) and \( f_2 \) entering a mixer, and the output frequencies \( f_1 \), \( f_2 \), \( f_1 + f_2 \), and \( |f_1 - f_2| \) exiting the mixer.