\subsection{Maximizing EME Connections: Finding the Best Path!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E3A03]
\textbf{E3A03} When scheduling EME contacts, which of these conditions will generally result in the least path loss?
\begin{enumerate}[label=\Alph*.]
    \item \textbf{When the Moon is at perigee}
    \item When the Moon is full
    \item When the Moon is at apogee
    \item When the MUF is above 30 MHz
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're trying to talk to someone on the Moon using a radio. The Moon doesn't always stay the same distance from Earth; sometimes it's closer, and sometimes it's farther away. When the Moon is closest to Earth (this is called perigee), your radio signal doesn't have to travel as far, so it doesn't lose as much strength. This means you have a better chance of making a clear connection. When the Moon is full or when it's farthest from Earth (called apogee), the signal has to travel a longer distance, so it gets weaker. The MUF (Maximum Usable Frequency) being above 30 MHz doesn't directly affect how far the signal has to travel, so it doesn't help reduce path loss.

\subsubsection{Advanced Explanation}
In Earth-Moon-Earth (EME) communications, path loss is a critical factor. Path loss is the reduction in power density of an electromagnetic wave as it propagates through space. The path loss \( L \) can be approximated by the Friis transmission equation:

\[
L = \left( \frac{4 \pi d}{\lambda} \right)^2
\]

where \( d \) is the distance between the transmitter and receiver, and \( \lambda \) is the wavelength of the signal. The Moon's distance from Earth varies due to its elliptical orbit. At perigee, the Moon is approximately 363,300 km from Earth, while at apogee, it is about 405,500 km away. 

Given that path loss is proportional to the square of the distance, the path loss is minimized when the Moon is at perigee. The phase of the Moon (full, new, etc.) does not affect the distance, and the MUF being above 30 MHz is unrelated to the distance between Earth and the Moon. Therefore, the least path loss occurs when the Moon is at perigee.

% Diagram Prompt: Generate a diagram showing the Moon's elliptical orbit around Earth, highlighting perigee and apogee, and indicating the path of a radio signal during EME communication.