\subsection{HF Bands with Phone Privileges for Technician Class Operators}
\label{T1B06}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T1B06]
On which HF bands does a Technician class operator have phone privileges?
\begin{enumerate}[label=\Alph*)]
    \item None
    \item \textbf{10 meter band only}
    \item 80 meter, 40 meter, 15 meter, and 10 meter bands
    \item 30 meter band only
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you’re a Technician class operator, and you’re given a special key to unlock certain doors in a big building called the HF bands. But here’s the catch: you only get to unlock one door—the 10 meter band. This is like having a VIP pass to only one concert in a music festival. So, while other operators might have access to more bands, you get to enjoy the 10 meter band for phone privileges. Think of it as your exclusive club where you can chat with other operators using voice communication.

\subsubsection{Advanced Explanation}
The HF (High Frequency) bands range from 3 to 30 MHz and are divided into several specific bands, each with its own frequency range and privileges. For Technician class operators, the FCC (Federal Communications Commission) grants phone (voice) privileges only on the 10 meter band, which spans from 28.000 MHz to 29.700 MHz. This is due to the regulatory framework that assigns different operating privileges to different license classes.

The 10 meter band is particularly suitable for Technician class operators because it supports both local and long-distance communication, especially during periods of good ionospheric propagation. Other HF bands, such as 80 meters (3.5–4.0 MHz), 40 meters (7.0–7.3 MHz), and 15 meters (21.0–21.45 MHz), are primarily allocated to higher license classes like General and Extra, who have broader privileges.

To summarize, the correct answer is \textbf{B: 10 meter band only}, as this is the only HF band where Technician class operators are permitted to use phone (voice) communication.

% Prompt for generating a diagram: A frequency spectrum diagram showing the HF bands and highlighting the 10 meter band with phone privileges for Technician class operators.