\subsection{Which VHF/UHF Band Segments Are Limited to CW Only?}
\label{T1B07}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T1B07]
Which of the following VHF/UHF band segments are limited to CW only?
\begin{enumerate}[label=\Alph*)]
    \item \textbf{50.0 MHz to 50.1 MHz and 144.0 MHz to 144.1 MHz}
    \item 219 MHz to 220 MHz and 420.0 MHz to 420.1 MHz
    \item 902.0 MHz to 902.1 MHz
    \item All these choices are correct
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine the radio spectrum as a big highway with different lanes. Some lanes are only for slow-moving vehicles (like bicycles), while others are for fast cars. In the radio world, CW (Continuous Wave) is like the slow-moving bicycle lane. It’s a simple, old-school way of sending messages using Morse code. The question is asking which parts of the radio highway are reserved just for these slow-moving CW signals. The correct answer is the 50.0 MHz to 50.1 MHz and 144.0 MHz to 144.1 MHz lanes. These segments are like the CW-only lanes where only Morse code is allowed.

\subsubsection{Advanced Explanation}
In the context of amateur radio, certain frequency bands are allocated exclusively for CW (Continuous Wave) transmission, which is primarily used for Morse code communication. The segments 50.0 MHz to 50.1 MHz and 144.0 MHz to 144.1 MHz are designated for CW-only operations. This allocation is based on international agreements and regulatory standards to ensure efficient use of the radio spectrum.

The frequency range 50.0 MHz to 50.1 MHz falls within the 6-meter band, while 144.0 MHz to 144.1 MHz is part of the 2-meter band. These segments are particularly suited for CW due to their propagation characteristics and historical usage patterns. CW is a narrowband mode, which means it requires very little bandwidth, making it ideal for these specific frequency ranges.

Other segments mentioned in the options, such as 219 MHz to 220 MHz, 420.0 MHz to 420.1 MHz, and 902.0 MHz to 902.1 MHz, are not exclusively limited to CW. They may be used for other modes of communication, including voice and digital modes.

% Diagram Prompt: Generate a diagram showing the VHF/UHF frequency bands with highlighted segments for CW-only operations.