\subsection{Health Hazards of Electrical Current}
\label{T0A02}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T0A02]
What health hazard is presented by electrical current flowing through the body?
\begin{enumerate}[label=\Alph*)]
    \item It may cause injury by heating tissue
    \item It may disrupt the electrical functions of cells
    \item It may cause involuntary muscle contractions
    \item \textbf{All these choices are correct}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine your body is like a big, squishy circuit. When electricity zaps through it, it can do all sorts of weird and not-so-fun things. It can cook your insides like a microwave (ouch!), mess with the tiny electrical signals that keep your heart and brain working (yikes!), and make your muscles twitch and jerk like a robot gone haywire (whoa!). So, yeah, electricity in your body is like a party crasher that ruins everything!

\subsubsection{Advanced Explanation}
Electrical current flowing through the human body can induce several physiological effects due to the body's conductive properties. The primary hazards include:

1. \textbf{Thermal Injury}: The resistance of body tissues to electrical current generates heat, which can cause burns and tissue damage. The power dissipated as heat can be calculated using Joule's Law:
   \[
   P = I^2 R
   \]
   where \( P \) is the power, \( I \) is the current, and \( R \) is the resistance of the tissue.

2. \textbf{Cellular Disruption}: Electrical currents can interfere with the normal electrical activity of cells, particularly in nerve and muscle cells. This can lead to arrhythmias in the heart or disrupt neural signaling in the brain.

3. \textbf{Muscle Contractions}: Electrical stimulation can cause involuntary muscle contractions, which can be dangerous if they affect the heart or respiratory muscles, potentially leading to cardiac arrest or respiratory failure.

All these effects are well-documented and contribute to the overall hazard posed by electrical current in the body. Therefore, the correct answer encompasses all these potential risks.

% Prompt for diagram: A diagram showing the path of electrical current through the human body, highlighting areas where thermal injury, cellular disruption, and muscle contractions occur.