\subsection{Fuse or Circuit Breaker Installation in 120V AC Power Circuit}
\label{T0A08}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T0A08]
Where should a fuse or circuit breaker be installed in a 120V AC power circuit?
\begin{enumerate}[label=\Alph*]
    \item \textbf{In series with the hot conductor only}
    \item In series with the hot and neutral conductors
    \item In parallel with the hot conductor only
    \item In parallel with the hot and neutral conductors
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a water pipe system in your house. The fuse or circuit breaker is like a safety valve that stops the water flow if there’s too much pressure. In a 120V AC power circuit, the hot wire is like the main pipe carrying the water (electricity). The safety valve (fuse or circuit breaker) should be placed in the main pipe (hot wire) to stop the flow if something goes wrong. Putting it in the neutral wire would be like putting the safety valve in the drain pipe—it wouldn’t help if the main pipe bursts!

\subsubsection{Advanced Explanation}
In a 120V AC power circuit, the hot conductor carries the current from the power source to the load, while the neutral conductor returns the current to the source. The purpose of a fuse or circuit breaker is to protect the circuit from overcurrent conditions, which can lead to overheating and potential fire hazards. 

To effectively interrupt the current flow during an overcurrent event, the fuse or circuit breaker must be placed in series with the hot conductor. This ensures that the circuit is broken and the current flow is stopped. Placing the fuse or circuit breaker in series with the neutral conductor would not provide the same level of protection, as the hot conductor would still carry current even if the neutral is interrupted.

Mathematically, the current \( I \) in a circuit is given by Ohm's Law:
\[
I = \frac{V}{R}
\]
where \( V \) is the voltage and \( R \) is the resistance. If the current exceeds the rated value of the fuse or circuit breaker, it will open the circuit, preventing further current flow and protecting the circuit components.

% Diagram prompt: Generate a diagram showing a 120V AC power circuit with a fuse or circuit breaker installed in series with the hot conductor.