\subsection{Lightning Arrester Installation in Coaxial Feed Line}
\label{T0A07}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T0A07]
Where should a lightning arrester be installed in a coaxial feed line?
\begin{enumerate}[label=\Alph*)]
    \item At the output connector of a transceiver
    \item At the antenna feed point
    \item At the ac power service panel
    \item \textbf{On a grounded panel near where feed lines enter the building}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine your coaxial feed line is like a water hose, and lightning is a giant splash of water. You want to protect your house from getting soaked, right? So, you put a special sponge (the lightning arrester) right where the hose enters your house. This sponge soaks up the big splash before it can get inside and cause a mess. That’s why the lightning arrester should be installed near where the feed lines enter the building—it’s the best spot to catch the lightning before it can do any damage!

\subsubsection{Advanced Explanation}
A lightning arrester is a device designed to protect electrical equipment from high-voltage surges caused by lightning strikes. In the context of a coaxial feed line, the arrester must be placed at a strategic location to effectively divert the surge to the ground. The optimal location is on a grounded panel near where the feed lines enter the building. This placement ensures that any lightning-induced surge is intercepted before it can propagate further into the building’s electrical system, thereby protecting sensitive equipment such as transceivers.

The arrester works by providing a low-impedance path to ground for the surge, effectively shunting the high voltage away from the equipment. The grounding of the panel is crucial, as it ensures that the surge energy is safely dissipated into the earth. Placing the arrester at the antenna feed point (option B) or at the output connector of a transceiver (option A) would not provide the same level of protection, as the surge could still propagate into the building’s wiring. Similarly, installing it at the AC power service panel (option C) would not protect the coaxial feed line specifically.

% Diagram prompt: A diagram showing the coaxial feed line entering a building, with the lightning arrester installed on a grounded panel near the entry point, and a path to ground indicated.