\subsection{Understanding Circuit Impedance: What Do the Axes Mean?}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E5C09] When using rectangular coordinates to graph the impedance of a circuit, what do the axes represent?
    \begin{enumerate}[label=\Alph*)]
        \item The X axis represents the resistive component, and the Y axis represents the reactive component
        \item The X axis represents the reactive component, and the Y axis represents the resistive component
        \item The X axis represents the phase angle, and the Y axis represents the magnitude
        \item The X axis represents the magnitude, and the Y axis represents the phase angle
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you are drawing a map of a circuit's impedance. The X-axis (horizontal) shows how much the circuit resists the flow of electricity, like a straight road. The Y-axis (vertical) shows how much the circuit reacts to changes in electricity, like a winding road. Together, they help us understand how the circuit behaves when electricity flows through it.

\subsubsection{Advanced Explanation}
In electrical engineering, impedance (\(Z\)) is a complex quantity that combines resistance (\(R\)) and reactance (\(X\)). When using rectangular coordinates, the impedance is represented as:
\[
Z = R + jX
\]
where \(R\) is the resistive component (real part) and \(X\) is the reactive component (imaginary part). The X-axis in the graph represents the resistive component (\(R\)), and the Y-axis represents the reactive component (\(X\)). This representation allows us to visualize the impedance in a way that separates its resistive and reactive behaviors.

The magnitude of the impedance (\(|Z|\)) and the phase angle (\(\theta\)) can be calculated from the rectangular coordinates using the following formulas:
\[
|Z| = \sqrt{R^2 + X^2}
\]
\[
\theta = \arctan\left(\frac{X}{R}\right)
\]
These calculations help in understanding the overall behavior of the circuit in terms of its opposition to the current and the phase difference between voltage and current.

% Diagram Prompt: Generate a diagram showing the rectangular coordinate system with the X-axis labeled as Resistive Component (R) and the Y-axis labeled as Reactive Component (X). Include a vector representing the impedance \(Z\) with its magnitude and phase angle.