\subsection{Understanding the Magic of Reactive Power!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black]
\textbf{E5D12} What is reactive power?  
\begin{enumerate}[label=\Alph*),noitemsep]
    \item Power consumed in circuit Q
    \item Power consumed by an inductor’s wire resistance
    \item The power consumed in inductors and capacitors
    \item \textbf{Wattless, nonproductive power}
\end{enumerate}
\end{tcolorbox}

\subsubsection*{Intuitive Explanation}
Imagine you have a toy car that you push back and forth on a table. Even though you are doing work by moving the car, the car doesn’t actually go anywhere—it just moves back and forth. Reactive power is like that! It’s the energy that moves back and forth in a circuit, especially in components like inductors and capacitors, but it doesn’t actually do any useful work like lighting a bulb or running a motor. That’s why it’s called wattless or nonproductive power.

\subsubsection*{Advanced Explanation}
Reactive power, denoted as \( Q \), is a concept in AC (alternating current) circuits where energy is stored and released by inductive and capacitive components. Unlike real power (\( P \)), which performs useful work, reactive power does not contribute to energy consumption but is necessary for maintaining the voltage levels in the system. It is mathematically expressed as:

\[
Q = V \cdot I \cdot \sin(\phi)
\]

where:
\begin{itemize}
    \item \( V \) is the voltage,
    \item \( I \) is the current,
    \item \( \phi \) is the phase angle between the voltage and current.
\end{itemize}

In inductors, energy is stored in the magnetic field, while in capacitors, it is stored in the electric field. This energy is exchanged between the source and the reactive components but does not perform any actual work. Reactive power is measured in volt-amperes reactive (VAR).

% Diagram Prompt: A diagram showing the relationship between real power (P), reactive power (Q), and apparent power (S) in a right-angled triangle, with the phase angle (φ) labeled.