\subsection{Hidden Transmitter Hunt Tools}
\label{T8C02}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T8C02]
Which of these items would be useful for a hidden transmitter hunt?
\begin{enumerate}[noitemsep]
    \item Calibrated SWR meter
    \item \textbf{A directional antenna}
    \item A calibrated noise bridge
    \item All these choices are correct
\end{enumerate}
\end{tcolorbox}

\subsubsection*{Intuitive Explanation}
Imagine you're playing a game of hide and seek, but instead of looking for a person, you're trying to find a hidden radio transmitter. To find it, you need something that can point you in the right direction. A directional antenna is like a compass that helps you zero in on the transmitter's location. The other tools listed, like the SWR meter and noise bridge, are more about tuning and measuring the radio itself, not finding it.

\subsubsection*{Advanced Explanation}
In a hidden transmitter hunt, the goal is to locate a concealed radio transmitter. A directional antenna is crucial because it allows you to determine the direction of the incoming signal. By rotating the antenna and observing the signal strength, you can triangulate the transmitter's position. 

An SWR meter measures the standing wave ratio, which is important for ensuring your antenna is properly tuned, but it doesn't help in locating a transmitter. Similarly, a noise bridge is used for impedance matching and is not designed for direction finding. Therefore, the most useful tool for a hidden transmitter hunt is a directional antenna.