\subsection{E9D10: Exploring the Cheerful Waves: Antenna Fun Below Resonance!}

\begin{tcolorbox}[colback=blue!5!white,colframe=blue!75!black]
    \textbf{E9D10} How does radiation resistance of a base-fed whip antenna change below its resonant frequency?
    \begin{enumerate}[label=\Alph*,noitemsep]
        \item Radiation resistance increases
        \item \textbf{Radiation resistance decreases}
        \item Radiation resistance becomes imaginary
        \item Radiation resistance does not depend on frequency
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're trying to make waves in a pool with a stick. If you move the stick at just the right speed, you create big, beautiful waves—this is like the antenna at its resonant frequency. But if you move the stick too slowly (below the resonant frequency), the waves become smaller and less energetic. Similarly, the radiation resistance of the antenna decreases because it's not as good at sending out waves when it's not at its happy frequency.

\subsubsection{Advanced Explanation}
The radiation resistance \( R_r \) of an antenna is a measure of how effectively it radiates electromagnetic energy. For a base-fed whip antenna, the radiation resistance is frequency-dependent. Below the resonant frequency, the antenna's electrical length becomes shorter relative to the wavelength of the signal. This results in a decrease in the radiation resistance.

Mathematically, the radiation resistance \( R_r \) can be approximated by:
\[
R_r \approx 80 \pi^2 \left( \frac{h}{\lambda} \right)^2
\]
where \( h \) is the height of the antenna and \( \lambda \) is the wavelength of the signal. As the frequency decreases, \( \lambda \) increases, causing \( \frac{h}{\lambda} \) to decrease. Consequently, \( R_r \) decreases as well.

This relationship highlights the importance of operating an antenna at or near its resonant frequency for optimal performance. Below resonance, the antenna's efficiency in radiating energy diminishes, leading to a lower radiation resistance.

% [Prompt for diagram: A graph showing the relationship between frequency and radiation resistance for a base-fed whip antenna, with a marked resonant frequency point.]