\subsection{CW Operator Transmission End Signal}
\label{G2C03}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G2C03]
What does it mean when a CW operator sends “KN” at the end of a transmission?
\begin{enumerate}[label=\Alph*),noitemsep]
    \item No US stations should call
    \item Operating full break-in
    \item \textbf{Listening only for a specific station or stations}
    \item Closing station now
\end{enumerate}
\end{tcolorbox}

\subsubsection*{Intuitive Explanation}
Imagine you're playing a game of tag, and you shout, Only my best friend can tag me now! That's kind of what a CW operator is doing when they send KN at the end of their transmission. They're saying, Hey, I'm only listening for a specific person or group to respond, so don't bother calling unless it's you!

\subsubsection*{Advanced Explanation}
In CW (Continuous Wave) communication, operators use specific procedural signals to manage the flow of communication. The signal KN is a procedural signal that indicates the operator is listening only for a specific station or stations to respond. This is particularly useful in crowded bands where multiple stations might be trying to communicate simultaneously. By sending KN, the operator is effectively reducing the number of potential responses, thereby minimizing interference and ensuring a clearer communication channel.

Mathematically, this can be represented as a filtering process where the operator's receiver is tuned to accept signals only from a specific set of stations, effectively reducing the noise and increasing the signal-to-noise ratio (SNR). The SNR can be expressed as:

\[
\text{SNR} = \frac{P_{\text{signal}}}{P_{\text{noise}}}
\]

where \( P_{\text{signal}} \) is the power of the desired signal and \( P_{\text{noise}} \) is the power of the noise. By limiting the number of responding stations, \( P_{\text{noise}} \) is reduced, thereby improving the SNR.

% Prompt for diagram: A diagram showing a CW operator sending KN and only specific stations responding, with arrows indicating the communication flow.