\subsection{Minimum Safe Distance from Power Lines for Antenna Installation}
\label{T0B06}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T0B06]
What is the minimum safe distance from a power line to allow when installing an antenna?
\begin{enumerate}[label=\Alph*)]
    \item Add the height of the antenna to the height of the power line and multiply by a factor of 1.5
    \item The height of the power line above ground
    \item 1/2 wavelength at the operating frequency
    \item \textbf{Enough so that if the antenna falls, no part of it can come closer than 10 feet to the power wires}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're flying a kite near power lines. You wouldn't want the kite to touch the wires, right? It's the same with antennas! When installing an antenna, you need to make sure that if it falls, it doesn't get too close to the power lines. The rule is simple: keep it at least 10 feet away. This way, even if the antenna takes a tumble, it won't cause any dangerous situations.

\subsubsection{Advanced Explanation}
The primary concern when installing an antenna near power lines is safety. Power lines carry high voltage, and any contact with them can result in severe electrical hazards, including electrocution or fires. The National Electrical Safety Code (NESC) and other regulatory bodies recommend maintaining a minimum clearance of 10 feet between any part of the antenna and the power lines. This distance ensures that even if the antenna collapses or falls, it will not come into contact with the power lines, thereby preventing potential accidents.

To calculate the safe distance, consider the height of the antenna and the height of the power lines. The key is to ensure that the sum of these heights, plus any additional factors (like the length of the antenna when it falls), does not bring the antenna within 10 feet of the power lines. This calculation is crucial for compliance with safety standards and for protecting both people and property.

% Prompt for diagram: A diagram showing an antenna installed at a safe distance from power lines, with a 10-foot clearance marked, would be helpful for visual understanding.