\subsection{Requirements for Climbing an Antenna Tower}
\label{T0B02}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T0B02]
What is required when climbing an antenna tower?
\begin{enumerate}[label=\Alph*)]
    \item Have sufficient training on safe tower climbing techniques
    \item Use appropriate tie-off to the tower at all times
    \item Always wear an approved climbing harness
    \item \textbf{All these choices are correct}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're climbing a really tall ladder, but instead of a ladder, it's a giant antenna tower. Now, you wouldn't just start climbing without knowing how to do it safely, right? You'd need to learn the right way to climb, make sure you're tied to the tower so you don't fall, and wear a special harness to keep you secure. So, when climbing an antenna tower, you need to do all these things to stay safe!

\subsubsection{Advanced Explanation}
Climbing an antenna tower involves several critical safety measures to prevent accidents and ensure the climber's safety. 

1. \textbf{Training on Safe Climbing Techniques}: Proper training ensures that the climber understands the risks and knows how to navigate the tower safely. This includes understanding the structure of the tower, recognizing potential hazards, and knowing how to use climbing equipment correctly.

2. \textbf{Appropriate Tie-Off}: Using a tie-off to the tower at all times is essential to prevent falls. This involves securing the climber to the tower using a lanyard or other safety device, which provides a fall arrest system in case of a slip or loss of balance.

3. \textbf{Approved Climbing Harness}: Wearing an approved climbing harness is mandatory. The harness distributes the climber's weight evenly and provides attachment points for safety lines and other equipment, ensuring that the climber remains secure throughout the ascent and descent.

All these measures are crucial and must be followed simultaneously to ensure maximum safety. Therefore, the correct answer is that all these choices are correct.

% Prompt for diagram: A diagram showing a climber on an antenna tower with safety harness, tie-off, and training equipment labeled could be helpful here.