\subsection{Reasons to Use Shielded Wire}
\label{T6D03}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T6D03]
Which of the following is a reason to use shielded wire?
\begin{enumerate}[label=\Alph*)]
    \item To decrease the resistance of DC power connections
    \item To increase the current carrying capability of the wire
    \item \textbf{To prevent coupling of unwanted signals to or from the wire}
    \item To couple the wire to other signals
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're trying to have a private conversation in a noisy room. You might use a soundproof booth to keep the noise out and your conversation in. Shielded wire works similarly! It acts like a protective barrier, keeping unwanted signals (like noise) from interfering with the signals traveling through the wire. So, just like the soundproof booth, shielded wire helps keep things clear and undisturbed.

\subsubsection{Advanced Explanation}
Shielded wire is designed to minimize electromagnetic interference (EMI) and radio frequency interference (RFI). The shield, typically made of a conductive material like braided copper, surrounds the inner conductor and acts as a barrier. This shield can be grounded to divert unwanted signals away from the inner conductor. 

The effectiveness of the shield can be quantified by its shielding effectiveness (SE), which is given by:

\[
SE = 20 \log_{10} \left( \frac{E_{\text{unshielded}}}{E_{\text{shielded}}} \right)
\]

where \( E_{\text{unshielded}} \) and \( E_{\text{shielded}} \) are the electric field strengths without and with the shield, respectively.

Shielded wire is particularly useful in environments with high levels of electromagnetic noise, such as near power lines, motors, or radio transmitters. It ensures that the signal integrity is maintained by preventing coupling of unwanted signals to or from the wire.

% Diagram prompt: Generate a diagram showing a cross-section of shielded wire, illustrating the inner conductor, insulation, and the outer shield.