\subsection{Common Visual Indicator}
\label{T6D07}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T6D07]
Which of the following is commonly used as a visual indicator?
\begin{enumerate}[label=\Alph*)]
    \item \textbf{LED}
    \item FET
    \item Zener diode
    \item Bipolar transistor
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a bunch of electronic components lying around, and you need something to show you when your circuit is working. You wouldn't use a tiny transistor or a diode that just sits there doing nothing visible, right? Instead, you'd use something that lights up, like a little bulb. In the world of electronics, that little bulb is called an LED (Light Emitting Diode). It’s like the Hey, I'm on! sign for your circuit. So, when you see an LED glowing, you know your circuit is alive and kicking!

\subsubsection{Advanced Explanation}
An LED, or Light Emitting Diode, is a semiconductor device that emits light when an electric current passes through it. The light emission occurs due to the recombination of electrons and holes within the semiconductor material, a process known as electroluminescence. LEDs are widely used as visual indicators in various electronic devices because of their low power consumption, long lifespan, and ability to emit light in different colors.

In contrast, a FET (Field-Effect Transistor), a Zener diode, and a bipolar transistor are not designed to emit light. A FET is used for amplifying or switching electronic signals, a Zener diode is used for voltage regulation, and a bipolar transistor is used for amplification or switching as well. None of these components have the capability to serve as a visual indicator.

Therefore, the correct answer is \textbf{LED}, as it is specifically designed to provide a visual indication of the circuit's status.

% Diagram Prompt: Generate a simple circuit diagram showing an LED connected to a power source with a resistor in series, illustrating how the LED lights up when the circuit is closed.