\subsection{Spotlight on Volunteer Examiner Coordinators!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E1E03] What is a Volunteer Examiner Coordinator?
    
    \begin{enumerate}[label=\Alph*),noitemsep]
        \item A person who has volunteered to administer amateur operator license examinations
        \item An organization paid by the volunteer examiner team to publicize and schedule examinations
        \item \textbf{An organization that has entered into an agreement with the FCC to coordinate, prepare, and administer amateur operator license examinations}
        \item The person who has entered into an agreement with the FCC to be the VE session manager
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you want to get a license to operate a ham radio. To get this license, you need to take a test. But who organizes these tests? That's where a Volunteer Examiner Coordinator (VEC) comes in. A VEC is like a group of people who work with the government (the FCC) to make sure these tests happen smoothly. They help set up the tests, make sure everything is fair, and send your results to the FCC. So, a VEC is not just one person, but an organization that helps you get your ham radio license.

\subsubsection{Advanced Explanation}
A Volunteer Examiner Coordinator (VEC) is an organization that has a formal agreement with the Federal Communications Commission (FCC) to oversee the administration of amateur radio license examinations. The VEC is responsible for coordinating the efforts of Volunteer Examiners (VEs), who are licensed amateur radio operators authorized to administer the exams. The VEC ensures that the exams are prepared according to FCC guidelines, schedules examination sessions, and processes the results to issue licenses. This system allows the FCC to delegate the examination process while maintaining regulatory oversight. The VEC acts as an intermediary between the FCC and the VEs, ensuring that the examination process is standardized and compliant with federal regulations.

% [Prompt for diagram: A flowchart showing the relationship between the FCC, VEC, VEs, and examinees, illustrating the process of administering amateur radio license examinations.]