\subsection{Rechargeable Battery Chemistries}
\label{T6A10}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T6A10]
Which of the following battery chemistries is rechargeable?
\begin{enumerate}[label=\Alph*)]
    \item Nickel-metal hydride
    \item Lithium-ion
    \item Lead-acid
    \item \textbf{All these choices are correct}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a toy car that runs on batteries. Some batteries, like the ones in your TV remote, you use once and throw away. But others, like the ones in your phone or laptop, you can charge over and over again. In this question, all the battery types listed—Nickel-metal hydride, Lithium-ion, and Lead-acid—are like the batteries in your phone. They can be recharged and used many times. So, the correct answer is that all of them are rechargeable!

\subsubsection{Advanced Explanation}
Battery chemistry determines whether a battery is rechargeable or not. Rechargeable batteries, also known as secondary batteries, can undergo reversible chemical reactions, allowing them to be recharged multiple times. 

1. \textbf{Nickel-metal hydride (NiMH)}: These batteries use a nickel oxide hydroxide cathode and a hydrogen-absorbing alloy anode. They are commonly used in portable electronics and hybrid vehicles due to their high energy density and ability to be recharged hundreds of times.

2. \textbf{Lithium-ion (Li-ion)}: These batteries use lithium ions moving between the anode and cathode to store and release energy. They are widely used in smartphones, laptops, and electric vehicles because of their high energy density, low self-discharge, and long cycle life.

3. \textbf{Lead-acid}: These are the oldest type of rechargeable battery, using lead dioxide as the cathode and metallic lead as the anode. They are commonly used in cars for starting, lighting, and ignition (SLI) due to their ability to deliver high surge currents.

All three chemistries—NiMH, Li-ion, and Lead-acid—are rechargeable, making the correct answer that all these choices are correct.

% Diagram Prompt: A diagram showing the internal structure and chemical reactions of NiMH, Li-ion, and Lead-acid batteries would be helpful for visual learners.