\subsection{Control Operator in RACES during Disaster}
\label{G2B09}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G2B09]
Who may be the control operator of an amateur station transmitting in RACES to assist relief operations during a disaster?
\begin{enumerate}[label=\Alph*)]
    \item \textbf{Only a person holding an FCC-issued amateur operator license}
    \item Only a RACES net control operator
    \item A person holding an FCC-issued amateur operator license or an appropriate government official
    \item Any control operator when normal communication systems are operational
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're in a superhero team during a disaster, and you need to use a special radio to call for help. But not just anyone can use this radio—only someone with a special license from the FCC (like a superhero badge) is allowed to operate it. This ensures that the person knows how to use the radio properly and can help effectively during the emergency. So, only the licensed superheroes can take charge of the radio in RACES!

\subsubsection{Advanced Explanation}
In the context of RACES (Radio Amateur Civil Emergency Service), the control operator of an amateur station must be someone who holds an FCC-issued amateur operator license. This requirement ensures that the operator has the necessary technical knowledge and legal authorization to operate the station, especially during critical situations like disasters. The FCC license signifies that the operator has passed the required examinations and is competent in radio communication protocols, which is crucial for effective and reliable communication during emergencies.

The other options are incorrect because:
\begin{itemize}
    \item Option B is incorrect because being a RACES net control operator alone does not necessarily mean the person holds an FCC-issued amateur license.
    \item Option C is incorrect because government officials, unless they also hold an FCC-issued amateur license, are not authorized to be control operators.
    \item Option D is incorrect because the control operator must always be licensed, regardless of the operational status of normal communication systems.
\end{itemize}

% Diagram prompt: A flowchart showing the hierarchy of who can be a control operator in RACES during a disaster, with FCC-licensed operators at the top.