\subsection{Discovering the Fun Differences: Direct FSK vs. Audio FSK!}
\label{sec:E2E11}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=\textbf{E2E11}]
\textbf{What is the difference between direct FSK and audio FSK?}
\begin{enumerate}[label=\Alph*.]
    \item \textbf{Direct FSK modulates the transmitter VFO}
    \item Direct FSK occupies less bandwidth
    \item Direct FSK can transmit higher baud rates
    \item All these choices are correct
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have two ways to send a message using radio waves. One way is like changing the pitch of your voice directly (Direct FSK), and the other way is like changing the pitch of a song playing on the radio (Audio FSK). Direct FSK changes the radio wave's frequency directly, while Audio FSK changes the frequency of a sound wave that is then sent through the radio. So, Direct FSK is like directly controlling the radio wave, while Audio FSK is like controlling a sound that the radio wave carries.

\subsubsection{Advanced Explanation}
Frequency Shift Keying (FSK) is a method of transmitting digital signals by changing the frequency of a carrier wave. There are two main types of FSK: Direct FSK and Audio FSK.

\begin{itemize}
    \item \textbf{Direct FSK}: In Direct FSK, the frequency of the transmitter's Voltage-Controlled Oscillator (VFO) is directly modulated by the digital signal. This means that the carrier wave's frequency is changed directly according to the input signal. Mathematically, if the carrier wave is represented as \( c(t) = A \cos(2\pi f_c t + \phi(t)) \), then in Direct FSK, \( f_c \) is varied directly by the digital signal.

    \item \textbf{Audio FSK}: In Audio FSK, the digital signal first modulates an audio frequency signal, which is then used to modulate the carrier wave. This means that the digital signal changes the frequency of an audio signal, and this audio signal is then used to modulate the carrier wave. Mathematically, if the audio signal is \( a(t) = A \cos(2\pi f_a t + \phi(t)) \), then in Audio FSK, \( f_a \) is varied by the digital signal, and this audio signal is then used to modulate the carrier wave.
\end{itemize}

The correct answer to the question is \textbf{A}, because Direct FSK directly modulates the transmitter's VFO, while Audio FSK modulates an audio signal that is then used to modulate the carrier wave.

% Prompt for generating a diagram:
% Diagram showing the difference between Direct FSK and Audio FSK, with Direct FSK directly modulating the VFO and Audio FSK modulating an audio signal that then modulates the carrier wave.