\subsection{Transponder Treasures: Unlocking Signal Secrets!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E2A07] Which of the following types of signals can be relayed through a linear transponder?
    \begin{enumerate}[label=\Alph*,noitemsep]
        \item FM and CW
        \item SSB and SSTV
        \item PSK and packet
        \item \textbf{All these choices are correct}
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine a linear transponder as a magical messenger that can carry different types of messages without changing them. Whether the message is a simple note (like CW), a conversation (like SSB), a picture (like SSTV), or even a coded message (like PSK and packet), the transponder can handle them all. It doesn’t pick favorites—it can relay all these types of signals just as they are!

\subsubsection{Advanced Explanation}
A linear transponder is designed to amplify and retransmit a wide range of input signals without altering their modulation characteristics. This means it can handle various signal types, including:

\begin{itemize}
    \item \textbf{FM (Frequency Modulation)}: A method where the frequency of the carrier wave is varied in accordance with the information signal.
    \item \textbf{CW (Continuous Wave)}: A simple on-off keying method used primarily for Morse code.
    \item \textbf{SSB (Single Sideband)}: A form of amplitude modulation where only one sideband is transmitted, reducing bandwidth and power consumption.
    \item \textbf{SSTV (Slow-Scan Television)}: A method for transmitting still images over radio frequencies.
    \item \textbf{PSK (Phase Shift Keying)}: A digital modulation scheme where the phase of the carrier wave is changed to represent data.
    \item \textbf{Packet}: A method of transmitting digital data in packets, often used in amateur radio for data communication.
\end{itemize}

Since a linear transponder does not discriminate between these modulation types, it can relay all of them effectively. This is why the correct answer is \textbf{D: All these choices are correct}.

% Prompt for diagram: A diagram showing a linear transponder receiving various signal types (FM, CW, SSB, SSTV, PSK, packet) and retransmitting them without alteration would be helpful here.