\subsection{On-the-Air Test Transmissions Requirements}
\label{T2A06}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T2A06]
Which of the following is required when making on-the-air test transmissions?
\begin{enumerate}[label=\Alph*)]
    \item \textbf{Identify the transmitting station}
    \item Conduct tests only between 10 p.m. and 6 a.m. local time
    \item Notify the FCC of the transmissions
    \item All these choices are correct
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're playing a game of hide and seek, but instead of hiding, you're shouting to find your friends. Now, if you just start shouting without telling anyone it's you, your friends might get confused or think it's someone else. Similarly, when you're testing your radio (shouting on the airwaves), you need to let everyone know it's you by identifying your station. This way, everyone knows who's talking and there's no confusion. So, always say, Hey, it's me, [your station name]! when you're testing your radio.

\subsubsection{Advanced Explanation}
In radio communications, it is a regulatory requirement to identify the transmitting station during on-the-air test transmissions. This is mandated by the Federal Communications Commission (FCC) to ensure transparency and accountability in the use of radio frequencies. The identification must include the station's call sign, which uniquely identifies the operator and the station. This practice helps in monitoring and managing the radio spectrum efficiently, preventing unauthorized use, and ensuring that all transmissions are traceable to their source.

The other options provided in the question are incorrect because:
\begin{itemize}
    \item Conducting tests only between 10 p.m. and 6 a.m. local time is not a requirement. Test transmissions can be made at any time, provided they comply with the regulations.
    \item Notifying the FCC of the transmissions is not necessary for routine test transmissions. However, certain types of special event stations or experimental operations may require prior notification or authorization.
    \item The option All these choices are correct is incorrect because only identifying the transmitting station is required.
\end{itemize}

% Prompt for generating a diagram: A flowchart showing the steps required for on-the-air test transmissions, including the identification of the transmitting station.