\subsection{Common Repeater Frequency Offset in the 2 Meter Band}
\label{T2A01}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T2A01]
What is a common repeater frequency offset in the 2 meter band?
\begin{enumerate}[label=\Alph*]
    \item Plus or minus 5 MHz
    \item \textbf{Plus or minus 600 kHz}
    \item Plus or minus 500 kHz
    \item Plus or minus 1 MHz
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you and your friend are trying to talk to each other, but you’re both using walkie-talkies. If you both talk at the same time, it’s just a big mess! So, you decide that one of you will talk on one channel, and the other will listen on a slightly different channel. This way, you can both talk without stepping on each other’s words. In the 2 meter band, this slightly different channel is usually 600 kHz away. That’s like moving just a tiny bit to the side so you can both chat without any confusion!

\subsubsection{Advanced Explanation}
In radio communication, repeaters are used to extend the range of communication by receiving a signal on one frequency and retransmitting it on another. The difference between these two frequencies is known as the frequency offset. In the 2 meter band (144-148 MHz), a common frequency offset is $\pm 600$ kHz. This offset ensures that the transmitted and received signals do not interfere with each other.

The choice of 600 kHz is based on practical considerations such as avoiding interference and ensuring compatibility with existing equipment. Mathematically, if the repeater receives a signal at frequency $f_r$, it will transmit the signal at frequency $f_t = f_r \pm 600$ kHz. This offset is standardized to maintain consistency across different repeater systems.

For example, if a repeater receives a signal at 145.000 MHz, it will transmit the signal at 145.600 MHz (for a $+600$ kHz offset) or at 144.400 MHz (for a $-600$ kHz offset). This ensures clear communication without overlapping frequencies.

% Diagram prompt: Generate a diagram showing the frequency offset in the 2 meter band, illustrating the input and output frequencies of a repeater with a 600 kHz offset.