\subsection{What Should You Do Before Calling CQ?}
\label{T2A12}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T2A12]
What should you do before calling CQ?
\begin{enumerate}[label=\Alph*)]
    \item Listen first to be sure that no one else is using the frequency
    \item Ask if the frequency is in use
    \item Make sure you are authorized to use that frequency
    \item \textbf{All these choices are correct}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you’re about to shout, Hey, anyone want to play? in a playground. Before you do, you’d probably look around to make sure no one else is already playing there, right? You might even ask, Is this spot taken? And of course, you’d want to make sure you’re allowed to be there in the first place! Calling CQ on a radio frequency is just like that. You need to listen first to make sure no one else is using the frequency, ask if it’s in use, and ensure you’re authorized to use it. So, all these steps are important before you start calling CQ!

\subsubsection{Advanced Explanation}
Before transmitting on any frequency, it is crucial to follow proper radio etiquette and regulations. Here’s a detailed breakdown of the steps:

1. \textbf{Listen First}: Tune your receiver to the frequency you intend to use and listen for any ongoing communications. This ensures that you do not interfere with existing transmissions, which is a fundamental principle of amateur radio operation.

2. \textbf{Ask if the Frequency is in Use}: If you are unsure whether the frequency is clear, you can politely ask, Is this frequency in use? This is a courteous way to confirm that you are not interrupting any ongoing communication.

3. \textbf{Ensure Authorization}: Verify that you are authorized to use the frequency. This involves checking the band plan and ensuring that your license class permits operation on that frequency. Unauthorized use can lead to interference and potential legal consequences.

By following these steps, you ensure that your transmission is respectful, legal, and does not cause interference to other operators. Therefore, all the given choices are correct.

% Diagram Prompt: A flowchart showing the steps to take before calling CQ could be helpful here.