\subsection{Least Reliable Bands for Long-Distance Communications}
\label{G3A04}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G3A04]
Which of the following are the least reliable bands for long-distance communications during periods of low solar activity?
\begin{enumerate}[label=\Alph*),noitemsep]
    \item 80 meters and 160 meters
    \item 60 meters and 40 meters
    \item 30 meters and 20 meters
    \item \textbf{15 meters, 12 meters, and 10 meters}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine the sun is like a giant battery that powers long-distance radio communications. When the sun is low on charge (low solar activity), some radio bands just don't work as well for talking to people far away. The higher frequency bands like 15 meters, 12 meters, and 10 meters are like weak walkie-talkies during these times—they’re the least reliable. So, if you’re trying to chat with someone across the globe during a low battery period, you might want to avoid these bands!

\subsubsection{Advanced Explanation}
The reliability of long-distance radio communications is heavily influenced by the ionosphere, which is affected by solar activity. During periods of low solar activity, the ionosphere is less ionized, particularly at higher altitudes. This reduces the ability of higher frequency bands (such as 15 meters, 12 meters, and 10 meters) to propagate signals over long distances via ionospheric reflection (skywave propagation).

The critical frequency \( f_c \) of the ionosphere is given by:
\[
f_c = \sqrt{80.8 \cdot N_e}
\]
where \( N_e \) is the electron density in the ionosphere. During low solar activity, \( N_e \) decreases, leading to a lower critical frequency. As a result, higher frequency bands (above the critical frequency) are less likely to be reflected by the ionosphere, making them unreliable for long-distance communications.

In contrast, lower frequency bands (such as 80 meters and 160 meters) can still propagate effectively because they are below the critical frequency even during low solar activity. Therefore, the higher frequency bands (15 meters, 12 meters, and 10 meters) are the least reliable for long-distance communications during these periods.

% Prompt for diagram: A diagram showing the ionospheric layers and how different frequency bands propagate during low solar activity would be helpful here.