\subsection{Voltage and Current Dance: Finding the Phase Angle in a Series RLC Circuit!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E5B11] What is the phase angle between the voltage across and the current through a series RLC circuit if \(X_C\) is 25 ohms, \(R\) is 100 ohms, and \(X_L\) is 75 ohms?
    \begin{enumerate}[label=\Alph*)]
        \item 27 degrees with the voltage lagging the current
        \item \textbf{27 degrees with the voltage leading the current}
        \item 63 degrees with the voltage lagging the current
        \item 63 degrees with the voltage leading the current
    \end{enumerate}
\end{tcolorbox}

\subsubsection*{Intuitive Explanation}
Imagine you have a dance floor where the voltage and current are dancing together. In a series RLC circuit, the voltage and current don't always move in sync. The phase angle tells us how much one is leading or lagging behind the other. In this case, the voltage is leading the current by 27 degrees. This means the voltage takes a step forward before the current does, like a dance move where one partner starts slightly earlier.

\subsubsection*{Advanced Explanation}
In a series RLC circuit, the phase angle \(\phi\) between the voltage and current can be calculated using the formula:
\[
\phi = \arctan\left(\frac{X_L - X_C}{R}\right)
\]
Given:
\[
X_L = 75 \, \Omega, \quad X_C = 25 \, \Omega, \quad R = 100 \, \Omega
\]
Substitute the values into the formula:
\[
\phi = \arctan\left(\frac{75 - 25}{100}\right) = \arctan\left(\frac{50}{100}\right) = \arctan(0.5)
\]
\[
\phi \approx 26.565^\circ \approx 27^\circ
\]
Since \(X_L > X_C\), the circuit is inductive, and the voltage leads the current by 27 degrees.

\subsubsection*{Related Concepts}
In an RLC circuit, the phase angle depends on the difference between the inductive reactance \(X_L\) and the capacitive reactance \(X_C\). If \(X_L > X_C\), the circuit is inductive, and the voltage leads the current. If \(X_C > X_L\), the circuit is capacitive, and the voltage lags the current. The resistance \(R\) affects the magnitude of the phase angle but not its direction.

% Diagram Prompt: Generate a diagram showing a series RLC circuit with labeled components (R, L, C) and arrows indicating the phase relationship between voltage and current.