\subsection{EchoLink System Requirements}
\label{T8C10}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T8C10]
What is required before using the EchoLink system?
\begin{enumerate}[label=\Alph*]
    \item Complete the required EchoLink training
    \item Purchase a license to use the EchoLink software
    \item \textbf{Register your call sign and provide proof of license}
    \item All these choices are correct
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you want to join a super cool club where everyone talks to each other using radios. But before you can join, you need to show your ID card (your call sign) and prove you’re allowed to be there (your license). That’s exactly what you need to do before using the EchoLink system! It’s like a secret handshake to get into the club.

\subsubsection{Advanced Explanation}
The EchoLink system is a network that allows licensed amateur radio operators to communicate over the internet. Before accessing this system, users must register their call sign and provide proof of their amateur radio license. This ensures that only licensed operators, who have passed the necessary examinations and are authorized to operate on amateur radio frequencies, can use the system. The registration process typically involves submitting your call sign and a copy of your license to the EchoLink administrators for verification. This step is crucial for maintaining the integrity and legality of the network.

% Diagram prompt: A flowchart showing the steps to register for EchoLink, including submitting call sign and license, and receiving access.