\subsection{Half-Wavelength Dipole Antenna Length}
\label{T9A09}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T9A09]
What is the approximate length, in inches, of a half-wavelength 6 meter dipole antenna?
\begin{enumerate}[label=\Alph*)]
    \item 6
    \item 50
    \item \textbf{112}
    \item 236
\end{enumerate}
\end{tcolorbox}

\subsubsection*{Intuitive Explanation}
Imagine you have a piece of string that’s 6 meters long. Now, if you want to make a simple antenna that’s half the length of a wave for a 6-meter radio signal, you’d cut the string in half, right? But wait, we need to convert meters to inches because the question asks for inches. There are about 39.37 inches in a meter. So, half of 6 meters is 3 meters, and 3 meters is about 118 inches. The closest answer is 112 inches. So, the antenna would be around 112 inches long. Easy peasy!

\subsubsection*{Advanced Explanation}
To determine the length of a half-wavelength dipole antenna for a 6-meter signal, we start by calculating the wavelength (\(\lambda\)) of the signal. The wavelength is given by the formula:

\[
\lambda = \frac{c}{f}
\]

where \(c\) is the speed of light (\(3 \times 10^8\) meters per second) and \(f\) is the frequency of the signal. For a 6-meter signal, the frequency is approximately:

\[
f = \frac{c}{\lambda} = \frac{3 \times 10^8}{6} = 50 \times 10^6 \text{ Hz} = 50 \text{ MHz}
\]

The length of a half-wavelength dipole antenna is half of the wavelength:

\[
\text{Half-wavelength} = \frac{\lambda}{2} = \frac{6}{2} = 3 \text{ meters}
\]

To convert meters to inches, we use the conversion factor \(1 \text{ meter} = 39.37 \text{ inches}\):

\[
3 \text{ meters} \times 39.37 \text{ inches/meter} = 118.11 \text{ inches}
\]

The closest answer to 118.11 inches is 112 inches, which corresponds to option C.

\subsubsection*{Related Concepts}
- \textbf{Wavelength (\(\lambda\))}: The distance between successive crests of a wave.
- \textbf{Frequency (\(f\))}: The number of wave cycles per second, measured in Hertz (Hz).
- \textbf{Dipole Antenna}: A type of antenna consisting of two conductive elements, typically used in radio and telecommunications.
- \textbf{Speed of Light (\(c\))}: The speed at which light travels in a vacuum, approximately \(3 \times 10^8\) meters per second.

% Diagram Prompt: Generate a diagram showing a 6-meter dipole antenna with its half-wavelength marked in inches.