\subsection{Advantage of a 5/8 Wavelength Whip Antenna}
\label{T9A12}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T9A12]
What is an advantage of a 5/8 wavelength whip antenna for VHF or UHF mobile service?
\begin{enumerate}[label=\Alph*)]
    \item \textbf{It has more gain than a 1/4-wavelength antenna}
    \item It radiates at a very high angle
    \item It eliminates distortion caused by reflected signals
    \item It has 10 times the power gain of a 1/4 wavelength whip
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're trying to shout across a field. If you use a tiny megaphone (like a 1/4-wavelength antenna), your voice won't carry very far. But if you use a bigger megaphone (like a 5/8-wavelength antenna), your voice will travel much farther because it’s more powerful. That’s the basic idea here—the 5/8-wavelength antenna is like a bigger megaphone for your radio signals, giving you more shout power (or gain) compared to the smaller one.

\subsubsection{Advanced Explanation}
The gain of an antenna is a measure of its ability to direct or concentrate radio frequency energy in a particular direction. A 5/8-wavelength whip antenna is designed to have a higher gain compared to a 1/4-wavelength antenna. This is because the 5/8-wavelength antenna has a more optimized radiation pattern, which allows it to focus more energy towards the horizon rather than wasting it in other directions.

The gain \( G \) of an antenna can be approximated using the formula:
\[
G = 10 \log_{10} \left( \frac{4 \pi A_e}{\lambda^2} \right)
\]
where \( A_e \) is the effective aperture of the antenna and \( \lambda \) is the wavelength of the signal. For a 5/8-wavelength antenna, the effective aperture is larger than that of a 1/4-wavelength antenna, resulting in higher gain.

Additionally, the 5/8-wavelength antenna has a lower radiation angle, which is beneficial for mobile services as it allows the signal to travel further along the ground rather than being wasted in the sky. This makes it particularly useful for VHF and UHF communications, where line-of-sight propagation is crucial.

% Diagram Prompt: Generate a diagram comparing the radiation patterns of a 1/4-wavelength antenna and a 5/8-wavelength antenna.