\subsection{Antenna Gain}
\label{T9A11}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T9A11]
What is antenna gain?  
\begin{enumerate}[label=\Alph*)]
    \item The additional power that is added to the transmitter power
    \item The additional power that is required in the antenna when transmitting on a higher frequency
    \item \textbf{The increase in signal strength in a specified direction compared to a reference antenna}
    \item The increase in impedance on receive or transmit compared to a reference antenna
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you’re at a concert, and the band is playing music. If you’re standing right in front of the speakers, the music sounds super loud and clear. But if you’re off to the side, it’s not as loud. Antenna gain is like the speakers focusing the music in one direction so it’s louder there compared to if the speakers were just spreading the sound everywhere equally. So, antenna gain is how much louder (stronger) the signal is in a specific direction compared to a basic antenna that sends signals equally in all directions.

\subsubsection{Advanced Explanation}
Antenna gain is a measure of how effectively an antenna directs or concentrates radio frequency energy in a particular direction compared to a reference antenna, typically an isotropic radiator (which radiates equally in all directions). The gain is usually expressed in decibels (dB) and is calculated using the following formula:

\[
G = 10 \log_{10} \left( \frac{P_{\text{max}}}{P_{\text{ref}}} \right)
\]

where \( G \) is the gain in dB, \( P_{\text{max}} \) is the maximum power radiated by the antenna in the desired direction, and \( P_{\text{ref}} \) is the power radiated by the reference antenna in the same direction.

Antenna gain is crucial in applications where signal strength in a specific direction is important, such as in point-to-point communication links or satellite communications. It is not about adding power to the transmitter but rather about focusing the existing power more effectively.

% Diagram prompt: Generate a diagram showing the radiation pattern of an isotropic antenna versus a directional antenna with gain, highlighting the focused signal strength in the desired direction.