\subsection{Half-Wave Dipole Antenna Radiation Direction}
\label{T9A10}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T9A10]
In which direction does a half-wave dipole antenna radiate the strongest signal?
\begin{enumerate}[label=\Alph*)]
    \item Equally in all directions
    \item Off the ends of the antenna
    \item In the direction of the feed line
    \item \textbf{Broadside to the antenna}
\end{enumerate}
\end{tcolorbox}

\subsubsection*{Intuitive Explanation}
Imagine you’re holding a jump rope and you start shaking it up and down. The waves you create move outward from the middle of the rope, not from the ends. A half-wave dipole antenna works similarly. The strongest signal doesn’t come from the ends or the feed line; it radiates outwards from the sides, like the waves from the middle of the jump rope. So, the signal is strongest broadside to the antenna, which means perpendicular to the antenna’s length.

\subsubsection*{Advanced Explanation}
A half-wave dipole antenna is a fundamental antenna design where the length of the antenna is approximately half the wavelength of the signal it is designed to transmit or receive. The radiation pattern of a half-wave dipole is characterized by a toroidal (doughnut-shaped) pattern, with the maximum radiation occurring in the plane perpendicular to the axis of the dipole. This direction is referred to as broadside to the antenna.

Mathematically, the radiation intensity \( U(\theta, \phi) \) of a half-wave dipole can be expressed as:
\[
U(\theta, \phi) = \frac{15 I_0^2}{\pi} \left( \frac{\cos\left(\frac{\pi}{2} \cos \theta\right)}{\sin \theta} \right)^2
\]
where \( I_0 \) is the peak current, \( \theta \) is the elevation angle, and \( \phi \) is the azimuth angle. The maximum radiation occurs when \( \theta = 90^\circ \), which is broadside to the antenna.

The radiation pattern is symmetric around the axis of the dipole, meaning the signal strength is uniform in all directions perpendicular to the antenna. This is why the strongest signal is radiated broadside to the antenna, and not off the ends or along the feed line.

% Diagram prompt: Generate a diagram showing the radiation pattern of a half-wave dipole antenna, highlighting the broadside direction.