\subsection{Calculating Cheerful Power: A 100-Ohm Circuit Adventure!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E5D11]
\textbf{E5D11} How much real power is consumed in a circuit consisting of a 100-ohm resistor in series with a 100-ohm inductive reactance drawing 1 ampere?
\begin{enumerate}[label=\Alph*]
    \item 70.7 watts
    \item \textbf{100 watts}
    \item 141.4 watts
    \item 200 watts
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a simple circuit with two parts: a resistor and an inductor. The resistor is like a narrow pipe that resists the flow of water, and the inductor is like a spinning wheel that stores energy. When electricity flows through this circuit, the resistor uses up some of the energy as heat, while the inductor stores some of it. The question is asking how much energy is actually used up by the resistor. Since the resistor is 100 ohms and the current is 1 ampere, the energy used up is simply 100 watts. The inductor doesn't use up any energy; it just stores it temporarily.

\subsubsection{Advanced Explanation}
In this circuit, we have a resistor \( R = 100 \, \Omega \) and an inductive reactance \( X_L = 100 \, \Omega \) in series, with a current \( I = 1 \, \text{A} \). The real power \( P \) consumed in the circuit is given by the formula:
\[
P = I^2 R
\]
Substituting the given values:
\[
P = (1 \, \text{A})^2 \times 100 \, \Omega = 100 \, \text{W}
\]
The inductive reactance \( X_L \) does not contribute to the real power consumption; it only affects the reactive power. Therefore, the real power consumed in the circuit is 100 watts.

\subsubsection{Related Concepts}
\begin{itemize}
    \item \textbf{Resistor}: A component that resists the flow of electric current, converting electrical energy into heat.
    \item \textbf{Inductive Reactance}: The opposition that an inductor presents to alternating current, which depends on the frequency of the current and the inductance of the inductor.
    \item \textbf{Real Power}: The actual power consumed by the resistive components in a circuit, measured in watts.
    \item \textbf{Reactive Power}: The power associated with the storage and release of energy by inductive and capacitive components, measured in volt-amperes reactive (VAR).
\end{itemize}

% Prompt for generating a diagram:
% A simple circuit diagram showing a resistor and an inductor in series with a current source labeled 1 A. The resistor is labeled 100 ohms, and the inductor is labeled 100 ohms inductive reactance.