\subsection{Waiting Game: When Can You Tune In?}
\label{sec:E1C03}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=Multiple Choice Question]
\textbf{E1C03} How long must an operator wait after filing a notification with the Utilities Technology Council (UTC) before operating on the 2200-meter or 630-meter band?

\begin{enumerate}[label=\Alph*,noitemsep]
    \item Operators must not operate until approval is received
    \item \textbf{Operators may operate after 30 days, providing they have not been told that their station is within 1 kilometer of PLC systems using those frequencies}
    \item Operators may not operate until a test signal has been transmitted in coordination with the local power company
    \item Operations may commence immediately, and may continue unless interference is reported by the UTC
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you want to play a new game, but before you start, you need to let the game organizers know. In this case, the game is using certain radio frequencies, and the organizers are the Utilities Technology Council (UTC). After you tell them you want to play, you have to wait for 30 days. If they don’t tell you that you’re too close to someone else’s game (like a power company’s system), you can start playing after those 30 days. It’s like waiting for permission, but if you don’t hear anything, you’re good to go!

\subsubsection{Advanced Explanation}
The 2200-meter and 630-meter bands are part of the radio spectrum that is shared with Power Line Carrier (PLC) systems, which are used by power companies for communication and control. To avoid interference, operators must notify the Utilities Technology Council (UTC) before using these frequencies. According to regulations, operators must wait for a period of 30 days after filing this notification. During this time, the UTC reviews the notification to ensure that the operator’s station is not within 1 kilometer of any PLC systems operating on the same frequencies. If no such notification is received within the 30-day period, the operator is permitted to commence operations. This waiting period allows for the identification and mitigation of potential interference issues, ensuring that both amateur radio operators and power companies can coexist without disrupting each other’s operations.

% Diagram Prompt: A flowchart showing the process of filing a notification with the UTC and the subsequent waiting period before operation can begin.