\subsection{Finding the Joyful Modulation Index of an FM Signal!}

\begin{tcolorbox}[colback=gray!10, colframe=black!80, title={Question ID: E8B04}]
What is the modulation index of an FM phone signal having a maximum carrier deviation of plus or minus 6 kHz if the highest modulating frequency is 2 kHz?
\begin{enumerate}[label=\Alph*.]
    \item 0.3
    \item \textbf{3}
    \item 0.6
    \item 6
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you are talking on a walkie-talkie. The sound of your voice causes the walkie-talkie's signal to change, like how a wave in the ocean goes up and down. The modulation index tells us how much the signal changes. In this question, the signal can change up to 6 kHz (like moving really high up and down). You are also making sound at a maximum of 2 kHz, which is like the highest wave of your voice. To find out how much your sound is changing the signal, we use the calculation called the modulation index (which is like measuring how tall the waves are compared to the highest one you made).

\subsubsection{Advanced Explanation}
The modulation index (\( \beta \)) in frequency modulation (FM) is defined as the ratio of the maximum frequency deviation of the carrier frequency (\( \Delta f \)) to the highest frequency of the modulating signal (\( f_m \)). Mathematically, it is represented as:

\[
\beta = \frac{\Delta f}{f_m}
\]

In this question, the maximum carrier deviation (\( \Delta f \)) is given as ±6 kHz, which can be simplified to 6 kHz for our calculation. The highest modulating frequency (\( f_m \)) is given as 2 kHz. Using the formula for modulation index, we substitute the values:

\[
\beta = \frac{\Delta f}{f_m} = \frac{6 \text{ kHz}}{2 \text{ kHz}} = 3
\]

Thus, the modulation index for the FM phone signal is 3. 

The modulation index is an important concept in telecommunication as it affects the bandwidth of the FM signal and the quality of the transmission. For example, a higher modulation index usually indicates a wider bandwidth and potentially better audio quality, but it also requires more bandwidth in radio frequency allocation.

% Prompt for diagram: Illustrate the concept of modulation index by showing a wave representing the carrier signal and how it deviates due to modulation, with labeled axes and crucial points.