\subsection{E9H09: Looping into Cheer: Unraveling Pennant Antenna Patterns!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=Question E9H09]
\textbf{E9H09} What type of radiation pattern is created by a single-turn, terminated loop such as a pennant antenna?
\begin{enumerate}[label=\Alph*.]
    \item \textbf{Cardioid}
    \item Bidirectional
    \item Omnidirectional
    \item Hyperbolic
\end{enumerate}
\end{tcolorbox}

\subsubsection*{Intuitive Explanation}
Imagine you’re at a football game, and you’re waving a pennant flag. The way the flag moves in the air is similar to how a pennant antenna radiates signals. Instead of sending signals in all directions like a cheerleader’s pom-poms (omnidirectional), or just back and forth like a referee’s whistle (bidirectional), the pennant antenna sends signals in a heart-shaped pattern, called a cardioid. This means it’s stronger in one direction and weaker in the opposite direction, just like how your cheer is louder in front of you and quieter behind you!

\subsubsection*{Advanced Explanation}
A single-turn, terminated loop antenna, such as a pennant antenna, generates a cardioid radiation pattern. This pattern is characterized by a single, dominant lobe that is shaped like a heart (hence the name cardioid). The cardioid pattern is a result of the constructive and destructive interference of the electromagnetic waves emitted by the antenna.

Mathematically, the radiation pattern \( P(\theta) \) of a cardioid can be expressed as:
\[
P(\theta) = 1 + \cos(\theta)
\]
where \( \theta \) is the angle relative to the direction of maximum radiation. This equation shows that the signal strength is maximum at \( \theta = 0^\circ \) and decreases as \( \theta \) increases, reaching zero at \( \theta = 180^\circ \).

The cardioid pattern is particularly useful in applications where it is desirable to minimize radiation in a specific direction, such as in certain types of communication systems where interference needs to be reduced.

% Diagram Prompt: Generate a diagram showing the cardioid radiation pattern of a pennant antenna, with labels indicating the direction of maximum and minimum radiation.