\subsection{E9H10: Boosting the Buzz: Enhancing Your Loop Antenna's Voltage!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=\textbf{E9H10}]
\textbf{How can the output voltage of a multiple-turn receiving loop antenna be increased?}
\begin{enumerate}[label=\Alph*)]
    \item By reducing the permeability of the loop shield
    \item By utilizing high impedance wire for the coupling loop
    \item \textbf{By increasing the number of turns and/or the area enclosed by the loop}
    \item All these choices are correct
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine your loop antenna is like a giant lasso catching radio waves. The bigger the lasso (the area of the loop) and the more times you spin it (the number of turns), the more radio waves you can catch. More waves mean more voltage, which is like having a louder signal. So, if you want to boost the buzz, make your lasso bigger and spin it more!

\subsubsection{Advanced Explanation}
The output voltage \( V \) of a multiple-turn receiving loop antenna is directly proportional to the number of turns \( N \) and the area \( A \) enclosed by the loop. This relationship can be expressed mathematically as:

\[
V \propto N \cdot A
\]

Where:
\begin{itemize}
    \item \( V \) is the output voltage,
    \item \( N \) is the number of turns,
    \item \( A \) is the area enclosed by the loop.
\end{itemize}

To increase the output voltage, you can either increase the number of turns \( N \) or increase the area \( A \) enclosed by the loop. This is because both factors contribute to the total magnetic flux \( \Phi \) intercepted by the loop, which in turn induces a higher voltage according to Faraday's Law of Induction:

\[
V = -N \frac{d\Phi}{dt}
\]

Where:
\begin{itemize}
    \item \( \Phi \) is the magnetic flux,
    \item \( \frac{d\Phi}{dt} \) is the rate of change of magnetic flux.
\end{itemize}

Therefore, increasing \( N \) or \( A \) will result in a higher output voltage, making option C the correct choice.

% Prompt for generating a diagram: 
% Diagram showing a loop antenna with multiple turns and a larger area, with arrows representing the magnetic flux and induced voltage.