\subsection{Exploring the Half-Power Bandwidth of a Resonant Circuit!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E5A11] What is the half-power bandwidth of a resonant circuit that has a resonant frequency of 7.1 MHz and a Q of 150?  
    \begin{enumerate}[label=\Alph*,noitemsep]
        \item 157.8 Hz
        \item 315.6 Hz
        \item \textbf{47.3 kHz}
        \item 23.67 kHz
    \end{enumerate}
\end{tcolorbox}

\subsubsection*{Intuitive Explanation}
Imagine you have a swing that swings back and forth at a specific speed. The resonant frequency is like the speed at which the swing naturally moves. The Q (quality factor) tells you how good the swing is at swinging at that speed without slowing down quickly. The half-power bandwidth is like the range of speeds around the natural speed where the swing still swings pretty well. In this case, the swing's natural speed is 7.1 MHz, and its Q is 150. The half-power bandwidth tells us how wide the range of speeds is where the swing still works well.

\subsubsection*{Advanced Explanation}
The half-power bandwidth (\(BW\)) of a resonant circuit is calculated using the formula:
\[
BW = \frac{f_r}{Q}
\]
where \(f_r\) is the resonant frequency and \(Q\) is the quality factor of the circuit.

Given:
\[
f_r = 7.1 \, \text{MHz} = 7.1 \times 10^6 \, \text{Hz}
\]
\[
Q = 150
\]

Substituting the values into the formula:
\[
BW = \frac{7.1 \times 10^6 \, \text{Hz}}{150} = 47.3 \times 10^3 \, \text{Hz} = 47.3 \, \text{kHz}
\]

Thus, the half-power bandwidth of the resonant circuit is \textbf{47.3 kHz}.

The Q factor is a measure of the sharpness of the resonance peak. A higher Q indicates a narrower bandwidth, meaning the circuit is more selective in the frequencies it responds to. The half-power bandwidth is the range of frequencies over which the power output is at least half of the maximum power output at the resonant frequency. This concept is crucial in designing filters and tuning circuits in radio technology.

% Prompt for diagram: A diagram showing the relationship between resonant frequency, Q factor, and half-power bandwidth would be helpful here.