\subsection{Finding the Fun: Half-Power Bandwidth of a Resonant Circuit!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E5A12] What is the half-power bandwidth of a resonant circuit that has a resonant frequency of 3.7 MHz and a Q of 118?
    \begin{enumerate}[label=\Alph*,noitemsep]
        \item 436.6 kHz
        \item 218.3 kHz
        \item \textbf{31.4 kHz}
        \item 15.7 kHz
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a swing that swings back and forth at a certain speed. The resonant frequency is like the speed at which the swing naturally wants to go. The Q (quality factor) tells us how good the swing is at swinging at that speed without slowing down too quickly. The half-power bandwidth is like the range of speeds around the natural speed where the swing still swings pretty well. In this case, the swing's natural speed is 3.7 MHz, and its Q is 118. We need to find out how wide the range of speeds is where the swing still works well.

\subsubsection{Advanced Explanation}
The half-power bandwidth (BW) of a resonant circuit can be calculated using the formula:
\[
\text{BW} = \frac{f_r}{Q}
\]
where \( f_r \) is the resonant frequency and \( Q \) is the quality factor of the circuit.

Given:
\[
f_r = 3.7 \, \text{MHz} = 3.7 \times 10^6 \, \text{Hz}
\]
\[
Q = 118
\]

Substituting the values into the formula:
\[
\text{BW} = \frac{3.7 \times 10^6 \, \text{Hz}}{118} \approx 31,355.93 \, \text{Hz} \approx 31.4 \, \text{kHz}
\]

Thus, the half-power bandwidth of the resonant circuit is approximately 31.4 kHz.

The Q factor is a measure of the sharpness of the resonance peak. A higher Q indicates a narrower bandwidth, meaning the circuit is more selective in the frequencies it responds to. The half-power bandwidth is the range of frequencies over which the circuit's response is at least half of its maximum value. This concept is crucial in designing filters and tuning circuits in radio technology.

% Diagram Prompt: Generate a diagram showing the frequency response of a resonant circuit with a resonant frequency of 3.7 MHz and a Q of 118, highlighting the half-power bandwidth.