\subsection{Increasing Transmitted Output Power}
\label{T7A10}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T7A10]
What device increases the transmitted output power from a transceiver?
\begin{enumerate}[label=\Alph*)]
    \item A voltage divider
    \item \textbf{An RF power amplifier}
    \item An impedance network
    \item All these choices are correct
\end{enumerate}
\end{tcolorbox}

\subsubsection*{Intuitive Explanation}
Imagine your transceiver is like a tiny speaker trying to shout across a football field. It’s just not loud enough! To make it louder, you need something like a megaphone. In the world of radio, that megaphone is called an RF power amplifier. It takes the weak signal from your transceiver and boosts it so it can travel farther and be heard clearly. So, if you want to increase the power of your transmitted signal, you need an RF power amplifier—not a voltage divider or an impedance network.

\subsubsection*{Advanced Explanation}
An RF (Radio Frequency) power amplifier is a device designed to increase the power of a signal in the radio frequency range. It takes a low-power RF signal from a transceiver and amplifies it to a higher power level suitable for transmission over long distances. The amplification process involves increasing the amplitude of the signal while maintaining its frequency and waveform characteristics.

Mathematically, the power gain \( G \) of an amplifier is given by:
\[
G = \frac{P_{\text{out}}}{P_{\text{in}}}
\]
where \( P_{\text{out}} \) is the output power and \( P_{\text{in}} \) is the input power. An RF power amplifier typically has a high power gain, making it essential for boosting the transmitted signal.

A voltage divider, on the other hand, is used to reduce voltage levels, not increase power. An impedance network is used to match impedances between different stages of a circuit to minimize signal reflection, but it does not inherently increase power. Therefore, the correct answer is an RF power amplifier.

% Diagram Prompt: Generate a diagram showing a transceiver connected to an RF power amplifier, with arrows indicating the flow of the signal and the increase in power.