\subsection{Test Equipment with Horizontal and Vertical Channel Amplifiers}
\label{G4B01}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G4B01]
What item of test equipment contains horizontal and vertical channel amplifiers?
\begin{enumerate}[label=\Alph*]
    \item An ohmmeter
    \item A signal generator
    \item An ammeter
    \item \textbf{An oscilloscope}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you’re trying to see a tiny, fast-moving bug on a piece of paper. You could use a magnifying glass, but what if the bug is moving so fast that you can’t keep up? You’d need something that can show you the bug’s path over time. That’s where an oscilloscope comes in! It’s like a super-powered magnifying glass for electrical signals. The horizontal and vertical channel amplifiers help the oscilloscope move the signal up, down, left, and right so you can see it clearly. So, if you’re looking for the tool that has these amplifiers, the oscilloscope is your best bet!

\subsubsection{Advanced Explanation}
An oscilloscope is a device used to visualize and analyze the waveform of electronic signals. It contains two main amplifiers: the horizontal (X-axis) and vertical (Y-axis) channel amplifiers. The vertical amplifier scales the input signal to fit the display, while the horizontal amplifier controls the time base, allowing the user to observe how the signal changes over time. 

Mathematically, if the input signal is \( V(t) \), the vertical amplifier scales it by a factor \( A_v \), and the horizontal amplifier scales the time axis by a factor \( A_h \). The displayed signal on the oscilloscope screen can be represented as:

\[
V_{\text{display}}(t) = A_v \cdot V(A_h \cdot t)
\]

This allows the oscilloscope to accurately represent both the amplitude and the time-dependent behavior of the signal. Other test equipment like ohmmeters, signal generators, and ammeters do not have these specific amplifiers, making the oscilloscope the correct answer.

% Prompt for diagram: A diagram showing the internal components of an oscilloscope, highlighting the horizontal and vertical channel amplifiers, would be beneficial here.