\subsection{Antenna Analyzer Measurements}
\label{G4B13}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G4B13]
Which of the following can be measured with an antenna analyzer?
\begin{enumerate}[label=\Alph*)]
    \item Front-to-back ratio of an antenna
    \item Power output from a transmitter
    \item \textbf{Impedance of coaxial cable}
    \item Gain of a directional antenna
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a magic wand that can tell you how well your radio antenna is talking to the airwaves. That’s kind of what an antenna analyzer does! It’s like a doctor for your antenna, checking its health. Now, out of the options, the antenna analyzer is really good at checking the impedance of a coaxial cable. Impedance is like the cable’s resistance to the radio signals passing through it. So, if you want to know if your cable is in good shape, the antenna analyzer is your go-to tool!

\subsubsection{Advanced Explanation}
An antenna analyzer is a versatile instrument used primarily to measure the impedance of antennas and transmission lines, such as coaxial cables. Impedance, denoted as \( Z \), is a complex quantity that combines resistance \( R \) and reactance \( X \), and is given by:
\[
Z = R + jX
\]
where \( j \) is the imaginary unit. The analyzer measures the impedance by sending a low-power RF signal through the cable and analyzing the reflected signal. This helps in determining the standing wave ratio (SWR) and ensuring that the antenna system is properly matched to the transmitter.

The other options, such as measuring the front-to-back ratio, power output, or gain of an antenna, typically require different specialized equipment. For instance, power output is measured using a wattmeter, while gain and front-to-back ratio are measured using field strength meters and directional antennas in controlled environments.

% Diagram prompt: Generate a diagram showing an antenna analyzer connected to a coaxial cable, with labels indicating the measurement of impedance.