\subsection{Inductance Insights: The Magic of Core Materials!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=\textbf{E6D11}]
\textbf{Which type of core material decreases inductance when inserted into a coil?}
\begin{enumerate}[label=\Alph*)]
    \item Ceramic
    \item \textbf{Brass}
    \item Ferrite
    \item Aluminum
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a coil of wire, like a spring. When you pass electricity through it, it creates a magnetic field, which is like an invisible force around the coil. Now, if you put something inside this coil, it can change how strong this magnetic field is. Some materials, like brass, don’t help the magnetic field at all. In fact, they can make it weaker. So, when you put brass inside the coil, the inductance (which is how much the coil can store magnetic energy) goes down. It’s like putting a block in the middle of a spring—it doesn’t let the spring stretch as much!

\subsubsection{Advanced Explanation}
Inductance (\(L\)) in a coil is influenced by the core material's permeability (\(\mu\)). The inductance is given by the formula:

\[
L = \frac{\mu N^2 A}{l}
\]

where:
\begin{itemize}
    \item \(\mu\) is the permeability of the core material,
    \item \(N\) is the number of turns in the coil,
    \item \(A\) is the cross-sectional area of the coil,
    \item \(l\) is the length of the coil.
\end{itemize}

Brass is a non-magnetic material with a permeability close to that of free space (\(\mu_0\)). When inserted into a coil, it does not enhance the magnetic flux, effectively reducing the overall inductance. In contrast, materials like ferrite have high permeability, which increases inductance. Therefore, brass decreases inductance when used as a core material.

% Diagram prompt: Generate a diagram showing a coil with different core materials (brass, ferrite, ceramic, aluminum) and their effect on the magnetic field strength.