\subsection{Voltmeter Connection for Voltage Measurement}
\label{T7D02}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T7D02]
How is a voltmeter connected to a component to measure applied voltage?
\begin{enumerate}[label=\Alph*)]
    \item In series
    \item \textbf{In parallel}
    \item In quadrature
    \item In phase
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're trying to measure how much water is flowing through a pipe. If you want to measure the pressure of the water at a specific point, you wouldn't cut the pipe and insert your measuring device in the middle, right? That would stop the flow! Instead, you'd attach your device to the side of the pipe to measure the pressure without interrupting the flow. Similarly, a voltmeter is connected in parallel to a component to measure the voltage without disrupting the circuit. It's like taking a sneak peek at the voltage without getting in the way!

\subsubsection{Advanced Explanation}
To measure the voltage across a component in an electrical circuit, a voltmeter must be connected in parallel with that component. This is because voltage is a potential difference between two points in a circuit. When connected in parallel, the voltmeter ensures that it measures the same potential difference as the component without altering the current flow through the circuit.

Mathematically, the voltage \( V \) across a component is given by Ohm's Law:
\[
V = I \cdot R
\]
where \( I \) is the current through the component and \( R \) is its resistance. By connecting the voltmeter in parallel, it effectively measures the voltage drop across the component without adding any significant resistance to the circuit.

Connecting the voltmeter in series would disrupt the circuit, as it would introduce an additional resistance, altering the current flow and thus the voltage measurement. Therefore, the correct method is to connect the voltmeter in parallel.

% Prompt for generating a diagram: 
% Create a simple circuit diagram showing a battery, a resistor, and a voltmeter connected in parallel across the resistor. Label the components clearly.