\subsection{Multimeter Measurements}
\label{T7D07}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T7D07]
Which of the following measurements are made using a multimeter?
\begin{enumerate}[label=\Alph*]
    \item Signal strength and noise
    \item Impedance and reactance
    \item \textbf{Voltage and resistance}
    \item All these choices are correct
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine a multimeter as a Swiss Army knife for electronics. It’s a handy tool that can measure different things, like how much push (voltage) is in a circuit or how much the circuit is fighting the flow of electricity (resistance). It’s not designed to measure how strong a signal is or how much noise is in the air, nor does it measure the tricky stuff like impedance and reactance. So, when you’re using a multimeter, think of it as your go-to tool for checking the basics: voltage and resistance.

\subsubsection{Advanced Explanation}
A multimeter is an essential instrument in electronics that combines several measurement functions into one unit. The primary measurements it can perform include voltage (V), current (I), and resistance (R). 

- \textbf{Voltage (V)}: This is the potential difference between two points in a circuit, measured in volts (V). A multimeter can measure both DC (direct current) and AC (alternating current) voltage.
  
- \textbf{Resistance (R)}: This is the opposition to the flow of electric current, measured in ohms ($\Omega$). A multimeter measures resistance by sending a small current through the component and measuring the voltage drop across it.

Multimeters are not typically used to measure signal strength, noise, impedance, or reactance. Signal strength and noise are usually measured with specialized equipment like spectrum analyzers. Impedance and reactance are more complex measurements that often require impedance analyzers or network analyzers.

In summary, the correct answer is \textbf{C}, as a multimeter is primarily used to measure voltage and resistance.

% Prompt for diagram: A diagram showing a multimeter measuring voltage and resistance in a simple circuit could be helpful here.