\subsection{Identification Requirements with FCC-Assigned Call Sign}\label{T1F02}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T1F02]
How often must you identify with your FCC-assigned call sign when using tactical call signs such as “Race Headquarters”?
\begin{enumerate}[label=\Alph*)]
    \item Never, the tactical call is sufficient
    \item Once during every hour
    \item \textbf{At the end of each communication and every ten minutes during a communication}
    \item At the end of every transmission
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're playing a game of hide-and-seek, but instead of hiding, you're using a special nickname like Race Headquarters to talk to your friends. The rules say that even though you're using this cool nickname, you still have to shout out your real name every once in a while so everyone knows it's really you. In this case, you need to say your real name (your FCC-assigned call sign) at the end of each conversation and every ten minutes while you're talking. This way, no one gets confused about who's really speaking!

\subsubsection{Advanced Explanation}
The Federal Communications Commission (FCC) requires that all amateur radio operators identify themselves using their assigned call sign to ensure transparency and accountability in communications. When using tactical call signs, such as Race Headquarters, the operator must still adhere to FCC regulations. Specifically, the operator must identify with their FCC-assigned call sign at the end of each communication and at least every ten minutes during a communication. This ensures that the operator's identity is periodically verified, maintaining the integrity of the communication process.

The regulation is designed to prevent misuse of the radio spectrum and to ensure that all communications can be traced back to a licensed operator. Failure to comply with these identification requirements can result in penalties, including fines or revocation of the operator's license.

% Diagram prompt: A timeline showing the points at which the FCC-assigned call sign must be announced during a communication using a tactical call sign.