\subsection{FCC Inspection Requirements for Station Records}
\label{T1F01}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T1F01]
When must the station and its records be available for FCC inspection?
\begin{enumerate}[label=\Alph*)]
    \item At any time ten days after notification by the FCC of such an inspection
    \item \textbf{At any time upon request by an FCC representative}
    \item At any time after written notification by the FCC of such inspection
    \item Only when presented with a valid warrant by an FCC official or government agent
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine the FCC (Federal Communications Commission) is like a school principal who can pop into your classroom at any time to check if you're following the rules. You don’t get a heads-up or a permission slip—they just show up and expect you to be ready. Similarly, radio stations must always be prepared to show their records to the FCC whenever asked. No delays, no excuses—just be ready!

\subsubsection{Advanced Explanation}
The FCC, as the regulatory body for communications in the United States, has the authority to inspect radio stations and their records to ensure compliance with federal regulations. According to FCC rules, stations must make their records available \textit{at any time} upon request by an FCC representative. This requirement is part of the FCC's enforcement mechanism to maintain the integrity and legality of radio communications. 

The correct answer, \textbf{B}, emphasizes the immediacy of this requirement. Unlike options A and C, which suggest a delay or formal notification, the FCC can request access without prior notice. Option D, which mentions a warrant, is incorrect because the FCC does not need a warrant to inspect a station’s records—it has statutory authority to do so under the Communications Act of 1934.

This rule underscores the importance of maintaining accurate and accessible records at all times, as non-compliance can result in penalties, fines, or even license revocation.

% Diagram prompt: A flowchart showing the FCC inspection process could help visualize the steps and requirements.