\subsection{Requirements for the Issuance of a Club Station License Grant}
\label{T1F11}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T1F11]
Which of the following is a requirement for the issuance of a club station license grant?
\begin{enumerate}[label=\Alph*]
    \item The trustee must have an Amateur Extra Class operator license grant
    \item \textbf{The club must have at least four members}
    \item The club must be registered with the American Radio Relay League
    \item All these choices are correct
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you and your friends want to start a club where you can all play with radios and talk to people far away. But before you can get a special license to do this, you need to make sure you have enough members in your club. The rule says you need at least four members. So, if you and three friends are ready to join, you’re good to go! It’s like needing a minimum number of players to start a game.

\subsubsection{Advanced Explanation}
In the context of amateur radio licensing, a club station license allows a group of licensed amateur radio operators to operate under a single call sign. The Federal Communications Commission (FCC) has specific requirements for issuing such a license. One of the key requirements is that the club must have at least four members. This ensures that the club is a legitimate group and not just an individual operating under the guise of a club.

Additionally, while the trustee of the club station does not necessarily need to hold an Amateur Extra Class operator license, they must be a licensed amateur radio operator. The club is also not required to be registered with the American Radio Relay League (ARRL), although many clubs choose to do so for the benefits it provides.

In summary, the correct requirement for the issuance of a club station license grant is that the club must have at least four members.

% Prompt for generating a diagram: A flowchart showing the requirements for a club station license grant, including the minimum number of members, trustee's license, and optional ARRL registration.