\subsection{Third-Party Agreement Message Restrictions}
\label{G1E05}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G1E05]
What are the restrictions on messages sent to a third party in a country with which there is a Third-Party Agreement?
\begin{enumerate}[label=\Alph*,noitemsep]
    \item They must relate to emergencies or disaster relief
    \item They must be for other licensed amateurs
    \item \textbf{They must relate to amateur radio, or remarks of a personal character, or messages relating to emergencies or disaster relief}
    \item The message must be limited to no longer than 1 minute in duration and the name of the third party must be recorded in the station log
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're sending a message to a friend in another country using your amateur radio. The rules say that your message can be about your radio hobby, something personal like Hey, how's your dog?, or even important stuff like There's a hurricane coming!. But you can't just send any random message like Buy this cool gadget! or Watch this movie!. The rules are there to keep the radio waves useful and not cluttered with ads or spam.

\subsubsection{Advanced Explanation}
In the context of amateur radio, a Third-Party Agreement allows licensed operators to transmit messages on behalf of individuals who are not licensed. However, these messages are subject to specific restrictions to ensure they align with the purpose of amateur radio. According to international regulations, such messages must pertain to amateur radio activities, contain personal remarks, or relate to emergencies or disaster relief. This ensures that the amateur radio spectrum is used appropriately and not for commercial or non-amateur purposes.

The correct answer, \textbf{C}, encompasses all permissible categories of messages under a Third-Party Agreement. This includes communications about amateur radio, personal messages, and emergency or disaster-related information. The other options either limit the scope too narrowly (A and B) or introduce irrelevant constraints (D).

% Diagram prompt: A flowchart showing the types of messages allowed under a Third-Party Agreement, with branches for amateur radio, personal remarks, and emergency/disaster relief.