\subsection{Retransmission Rules for 10-Meter Repeaters}
\label{G1E02}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G1E02]
When may a 10-meter repeater retransmit the 2-meter signal from a station that has a Technician class control operator?
\begin{enumerate}[label=\Alph*,noitemsep]
    \item Under no circumstances
    \item Only if the station on 10-meters is operating under a Special Temporary Authorization allowing such retransmission
    \item Only during an FCC-declared general state of communications emergency
    \item \textbf{Only if the 10-meter repeater control operator holds at least a General class license}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a walkie-talkie that can talk to another walkie-talkie on a different channel. Now, if you want to use a big, powerful radio (the 10-meter repeater) to repeat what you're saying on your smaller radio (the 2-meter signal), there's a rule: the person in charge of the big radio needs to have a special license (at least a General class license). It's like needing a driver's license to drive a car—you can't just hop in and go without one!

\subsubsection{Advanced Explanation}
In the context of amateur radio, the FCC (Federal Communications Commission) has specific rules governing the operation of repeaters, especially when it comes to retransmitting signals across different frequency bands. A 10-meter repeater operates in the 28.000-29.700 MHz range, while a 2-meter signal operates in the 144-148 MHz range. 

According to FCC regulations, a 10-meter repeater can retransmit a 2-meter signal only if the control operator of the 10-meter repeater holds at least a General class license. This ensures that the operator has the necessary knowledge and skills to manage the repeater responsibly. 

The General class license requires passing a more advanced exam than the Technician class, covering topics such as operating practices, rules, and more complex technical knowledge. This regulation helps maintain order and prevents misuse of the radio spectrum.

% Diagram Prompt: Generate a diagram showing the flow of signals from a 2-meter station to a 10-meter repeater, highlighting the control operator's license requirement.