\subsection{Exemption of Digital Mode Messages from Part 97 Third-Party Rules}
\label{G1E09}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G1E09]
Under what circumstances are messages that are sent via digital modes exempt from Part 97 third-party rules that apply to other modes of communication?
\begin{enumerate}[label=\Alph*)]
    \item \textbf{Under no circumstances}
    \item When messages are encrypted
    \item When messages are not encrypted
    \item When under automatic control
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're playing a game where you have to follow certain rules when passing messages to your friends. Now, if you decide to use a secret code (like a digital mode) to send these messages, you might think the rules don't apply anymore. But guess what? The rules are like your parents' rules—they apply no matter how you send the message! So, even if you're using a digital mode, you still have to follow the same rules as everyone else. No sneaky exceptions here!

\subsubsection{Advanced Explanation}
The Part 97 rules, established by the Federal Communications Commission (FCC), govern amateur radio operations in the United States. These rules include specific provisions regarding third-party communications, which are messages sent by an amateur radio operator on behalf of someone else. 

Digital modes, which encode messages in a digital format for transmission, are subject to the same Part 97 rules as other modes of communication. This means that regardless of whether the message is encrypted, unencrypted, or sent under automatic control, the third-party rules still apply. 

The correct answer, \textbf{A}, emphasizes that there are no circumstances under which digital mode messages are exempt from these rules. This ensures consistency and fairness in amateur radio communications, preventing any potential misuse or circumvention of the established regulations.

% Prompt for diagram: A flowchart showing the application of Part 97 rules to different modes of communication, including digital modes, could help visualize the concept.