\subsection{Unlocking the Mystery of Voltage Peaks in RLC Circuits!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E5A01] What can cause the voltage across reactances in a series RLC circuit to be higher than the voltage applied to the entire circuit?
    \begin{enumerate}[label=\Alph*.]
        \item \textbf{Resonance}
        \item Capacitance
        \item Low quality factor (Q)
        \item Resistance
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you are pushing a swing. If you push it at just the right time, the swing goes higher and higher. This is similar to what happens in an RLC circuit at resonance. When the circuit is at resonance, the voltage across the reactances (like the swing going higher) can be much larger than the voltage you applied to the circuit (like your push). This happens because the energy in the circuit is being transferred back and forth between the inductor and the capacitor very efficiently, causing the voltage to build up.

\subsubsection{Advanced Explanation}
In a series RLC circuit, the impedance \( Z \) is given by:
\[
Z = R + j\left(\omega L - \frac{1}{\omega C}\right)
\]
where \( R \) is the resistance, \( L \) is the inductance, \( C \) is the capacitance, and \( \omega \) is the angular frequency of the applied voltage. At resonance, the inductive reactance \( \omega L \) and the capacitive reactance \( \frac{1}{\omega C} \) are equal, causing the imaginary part of the impedance to cancel out:
\[
\omega L = \frac{1}{\omega C}
\]
This results in the impedance being purely resistive, \( Z = R \). However, the voltage across the inductor \( V_L \) and the capacitor \( V_C \) can be much higher than the applied voltage \( V \) due to the quality factor \( Q \):
\[
Q = \frac{\omega_0 L}{R} = \frac{1}{\omega_0 C R}
\]
where \( \omega_0 \) is the resonant frequency. The voltages across the inductor and capacitor are given by:
\[
V_L = V_C = QV
\]
Thus, at resonance, the voltage across the reactances can be significantly higher than the applied voltage, especially in circuits with a high quality factor.

% Diagram Prompt: Generate a diagram showing a series RLC circuit with labeled components (R, L, C) and the applied voltage V, with arrows indicating the voltages across the inductor and capacitor.