\subsection{Resistor Connections: Boosting Power Supply Harmony!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E7D14] What is the purpose of connecting equal-value resistors across power supply filter capacitors connected in series?
    \begin{enumerate}[label=\Alph*),noitemsep]
        \item Equalize the voltage across each capacitor
        \item Discharge the capacitors when voltage is removed
        \item Provide a minimum load on the supply
        \item \textbf{All these choices are correct}
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a series of water tanks connected together, and you want to make sure each tank has the same amount of water. If you connect pipes with equal resistance between the tanks, the water will flow evenly, balancing the levels. Similarly, in a power supply, connecting equal-value resistors across series capacitors ensures that the voltage is evenly distributed across each capacitor. Additionally, these resistors help safely discharge the capacitors when the power is turned off, and they provide a small, steady load to keep the power supply stable.

\subsubsection{Advanced Explanation}
When capacitors are connected in series, the voltage across each capacitor can vary due to differences in their capacitance or leakage currents. By connecting equal-value resistors across each capacitor, we ensure that the voltage is evenly distributed. This is because the resistors form a voltage divider network, balancing the voltage across each capacitor. 

Mathematically, if \( V_{\text{total}} \) is the total voltage across the series capacitors, and \( R \) is the resistance of each resistor, the voltage across each capacitor \( V_i \) is given by:
\[
V_i = \frac{V_{\text{total}}}{n}
\]
where \( n \) is the number of capacitors in series.

Additionally, these resistors provide a discharge path for the capacitors when the power is removed, ensuring safety by preventing residual voltage. They also act as a minimum load on the power supply, stabilizing the output voltage.

% Diagram Prompt: Generate a diagram showing series capacitors with equal-value resistors connected across each capacitor, illustrating the voltage distribution and discharge paths.