\subsection{Spot the Super Solar Flare!}
\label{sec:E3C07}

\begin{tcolorbox}[colback=blue!5!white,colframe=blue!75!black]
    \textbf{E3C07} Which of the following indicates the greatest solar flare intensity?
    \begin{enumerate}[label=\Alph*]
        \item Class A
        \item Class Z
        \item Class M
        \item \textbf{Class X}
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine the Sun as a giant ball of energy that sometimes sends out bursts of light and energy called solar flares. These flares can be small, medium, or super big. Scientists have a way of measuring how strong these flares are, and they use letters to describe them. Just like in school, where an A is good, but an X is even better, the Sun's flares are labeled with letters too. The biggest and strongest flares are called Class X. So, if you want to spot the super solar flare, look for the one labeled Class X!

\subsubsection{Advanced Explanation}
Solar flares are classified based on their peak flux in the soft X-ray wavelength range (1 to 8 Ångströms) as measured by the GOES (Geostationary Operational Environmental Satellite) spacecraft. The classification system uses letters to denote the order of magnitude of the flare's intensity:

\begin{itemize}
    \item \textbf{Class A}: Flares with a peak flux of less than \(10^{-7}\) watts per square meter (W/m\(^2\)).
    \item \textbf{Class B}: Flares with a peak flux between \(10^{-7}\) and \(10^{-6}\) W/m\(^2\).
    \item \textbf{Class C}: Flares with a peak flux between \(10^{-6}\) and \(10^{-5}\) W/m\(^2\).
    \item \textbf{Class M}: Flares with a peak flux between \(10^{-5}\) and \(10^{-4}\) W/m\(^2\).
    \item \textbf{Class X}: Flares with a peak flux greater than \(10^{-4}\) W/m\(^2\).
\end{itemize}

The classification is logarithmic, meaning each step represents a tenfold increase in intensity. For example, a Class X flare is ten times more intense than a Class M flare. Therefore, the greatest solar flare intensity is indicated by \textbf{Class X}.

% Diagram prompt: Generate a diagram showing the classification of solar flares with their corresponding peak flux ranges and examples of each class.