\subsection{FCC Part 97 Definition of a Space Station}
\label{T1A07}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T1A07]
What is the FCC Part 97 definition of a space station?
\begin{enumerate}[label=\Alph*)]
    \item Any satellite orbiting Earth
    \item A manned satellite orbiting Earth
    \item \textbf{An amateur station located more than 50 km above Earth's surface}
    \item An amateur station using amateur radio satellites for relay of signals
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a walkie-talkie, but instead of using it on the ground, you take it up in a hot air balloon. If you go really high—more than 50 kilometers above the Earth—your walkie-talkie becomes a space station according to the FCC. It’s not about being a satellite or having astronauts; it’s all about how high you are! And by "high", we don't mean that kind of "high".

\subsubsection{Advanced Explanation}
The Federal Communications Commission (FCC) Part 97 rules govern amateur radio operations in the United States. According to these rules, a space station is specifically defined as an amateur station located more than 50 kilometers above the Earth's surface. This definition is crucial because it distinguishes amateur radio operations in space from other types of satellite operations. The 50 km threshold is significant as it marks the boundary where the Earth's atmosphere becomes extremely thin, and traditional ground-based communication methods are no longer effective. 

The FCC's definition does not require the station to be a satellite or to be manned. It simply focuses on the altitude at which the amateur station operates. This allows amateur radio operators to engage in high-altitude balloon projects or other high-altitude experiments without needing to meet the more stringent requirements associated with satellite operations.

% Diagram Prompt: Generate a diagram showing the Earth's atmosphere layers with the 50 km threshold marked, illustrating where a space station would be located.