\subsection{Velocity of Radio Waves in Free Space}
\label{T3B04}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T3B04]
What is the velocity of a radio wave traveling through free space?
\begin{enumerate}[label=\Alph*)]
    \item \textbf{Speed of light}
    \item Speed of sound
    \item Speed inversely proportional to its wavelength
    \item Speed that increases as the frequency increases
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're playing a game of tag with your friends, and you're it. You run as fast as you can to catch someone. Now, think of a radio wave as a super-fast runner that never gets tired. In free space, which is like a giant, empty playground, the radio wave runs at the speed of light—the fastest speed possible! It doesn't matter if the wave is long or short, or if it's high-pitched or low-pitched; it always runs at the same speed. So, the correct answer is the speed of light, because that's how fast radio waves zoom through space!

\subsubsection{Advanced Explanation}
The velocity of a radio wave in free space is determined by the fundamental properties of electromagnetic waves. In free space, the speed of an electromagnetic wave, including radio waves, is given by the equation:

\[
v = \frac{1}{\sqrt{\mu_0 \epsilon_0}}
\]

where:
\begin{itemize}
    \item \( v \) is the velocity of the wave,
    \item \( \mu_0 \) is the permeability of free space (\( 4\pi \times 10^{-7} \, \text{H/m} \)),
    \item \( \epsilon_0 \) is the permittivity of free space (\( 8.854 \times 10^{-12} \, \text{F/m} \)).
\end{itemize}

When we plug in the values for \( \mu_0 \) and \( \epsilon_0 \), we find that:

\[
v = \frac{1}{\sqrt{(4\pi \times 10^{-7}) (8.854 \times 10^{-12})}} \approx 3 \times 10^8 \, \text{m/s}
\]

This value is the speed of light, denoted by \( c \). Therefore, the velocity of a radio wave in free space is equal to the speed of light. This is a fundamental result in electromagnetism and is independent of the wavelength or frequency of the radio wave.

% Prompt for diagram: A diagram showing a radio wave traveling through free space with labels indicating the speed of light and the wave's wavelength and frequency.