\subsection{Velocity of Radio Waves in Free Space}
\label{T3B11}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T3B11]
What is the approximate velocity of a radio wave in free space?
\begin{enumerate}[label=\Alph*)]
    \item 150,000 meters per second
    \item \textbf{300,000,000 meters per second}
    \item 300,000,000 miles per hour
    \item 150,000 miles per hour
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you’re playing a game of tag with your friends, and you’re the fastest runner in the group. Now, think of a radio wave as a super-speedy runner that doesn’t get tired. In the vast open space (like outer space), this runner can zoom at an incredible speed—about 300,000,000 meters per second! That’s so fast that it could circle the Earth about 7.5 times in just one second. So, when we talk about radio waves in free space, they’re like the Usain Bolt of the electromagnetic world, zipping along at this mind-blowing speed.

\subsubsection{Advanced Explanation}
The velocity of a radio wave in free space is determined by the fundamental properties of electromagnetic waves. In free space, the speed of an electromagnetic wave, including radio waves, is given by the equation:

\[
v = \frac{1}{\sqrt{\mu_0 \epsilon_0}}
\]

where:
\begin{itemize}
    \item \( v \) is the velocity of the wave,
    \item \( \mu_0 \) is the permeability of free space (\( 4\pi \times 10^{-7} \, \text{H/m} \)),
    \item \( \epsilon_0 \) is the permittivity of free space (\( 8.854 \times 10^{-12} \, \text{F/m} \)).
\end{itemize}

Substituting the values of \( \mu_0 \) and \( \epsilon_0 \) into the equation:

\[
v = \frac{1}{\sqrt{(4\pi \times 10^{-7}) (8.854 \times 10^{-12})}}
\]

\[
v \approx 3 \times 10^8 \, \text{meters per second}
\]

This value is commonly approximated as 300,000,000 meters per second, which is the speed of light in a vacuum. Since radio waves are a type of electromagnetic wave, they travel at this same speed in free space.

% Diagram prompt: A diagram showing the propagation of radio waves in free space, with arrows indicating the direction of wave travel and labels for the speed of light.