\subsection{Satellite Beacon Telemetry Information}
\label{T8B01}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T8B01]
What telemetry information is typically transmitted by satellite beacons?
\begin{enumerate}[label=\Alph*)]
    \item The signal strength of received signals
    \item Time of day accurate to plus or minus 1/10 second
    \item \textbf{Health and status of the satellite}
    \item All these choices are correct
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine a satellite as a spaceship floating in space. Just like how you might send a text message to your friend to let them know you're doing okay, satellites send out little messages called beacons. These beacons tell us how the satellite is feeling—kind of like a health check-up. So, when we ask what kind of info these beacons send, it's mostly about the satellite's health and status, not about how strong the signals are or the exact time.

\subsubsection{Advanced Explanation}
Satellite beacons are crucial for monitoring the operational status of satellites. They transmit telemetry data, which includes information about the satellite's health and status. This data can encompass various parameters such as battery voltage, temperature, power consumption, and the functionality of onboard systems. 

The correct answer, \textbf{C}, highlights that the primary purpose of these beacons is to provide health and status information. This is essential for ground control to ensure the satellite is functioning correctly and to take corrective actions if necessary. 

While options A and B might seem plausible, they are not the primary focus of satellite beacons. Option A refers to signal strength, which is more relevant to ground-based receivers rather than the satellite itself. Option B mentions time accuracy, which, although important for synchronization, is not the main telemetry data transmitted by beacons. Option D is incorrect because not all the listed choices are typically transmitted by satellite beacons.

% Diagram prompt: A diagram showing a satellite transmitting a beacon signal to a ground station, with labels indicating the health and status information being sent.