\subsection{Doppler Shift in Satellite Communications}
\label{T8B07}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T8B07]
What is Doppler shift in reference to satellite communications?
\begin{enumerate}[label=\Alph*)]
    \item A change in the satellite orbit
    \item A mode where the satellite receives signals on one band and transmits on another
    \item \textbf{An observed change in signal frequency caused by relative motion between the satellite and Earth station}
    \item A special digital communications mode for some satellites
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're standing on the ground, and a friend is riding a bike towards you while ringing a bell. As your friend gets closer, the bell sounds higher-pitched. But as they ride away, the bell sounds lower-pitched. This change in pitch is similar to what happens with radio signals in satellite communications. When a satellite is moving towards or away from an Earth station, the frequency of the signal changes slightly. This is called the Doppler shift. It's like the satellite is ringing a bell with its radio signals, and the pitch changes depending on whether it's coming closer or moving away.

\subsubsection{Advanced Explanation}
The Doppler shift, or Doppler effect, is a phenomenon where the frequency of a wave changes due to the relative motion between the source and the observer. In satellite communications, the satellite and the Earth station are in relative motion, which causes a shift in the frequency of the transmitted signal. Mathematically, the observed frequency \( f' \) can be calculated using the formula:

\[
f' = f \left( \frac{c + v_r}{c + v_s} \right)
\]

where:
\begin{itemize}
    \item \( f \) is the original frequency of the signal,
    \item \( c \) is the speed of light,
    \item \( v_r \) is the velocity of the receiver (Earth station) relative to the medium,
    \item \( v_s \) is the velocity of the source (satellite) relative to the medium.
\end{itemize}

If the satellite is moving towards the Earth station, \( v_s \) is positive, and the observed frequency increases. If the satellite is moving away, \( v_s \) is negative, and the observed frequency decreases. This shift must be accounted for in satellite communication systems to ensure accurate signal reception.

% Diagram Prompt: Generate a diagram showing a satellite moving towards and away from an Earth station, with arrows indicating the direction of motion and the corresponding frequency shifts.