\subsection{Discover the Magic of Voltage-Controlled Capacitors!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E6B04] What type of semiconductor device is designed for use as a voltage-controlled capacitor?
    \begin{enumerate}[label=\Alph*),noitemsep]
        \item \textbf{Varactor diode}
        \item Tunnel diode
        \item Silicon-controlled rectifier
        \item Zener diode
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a magical device that can change its ability to store electricity just by adjusting the voltage you apply to it. This is exactly what a voltage-controlled capacitor does! Among the options, the varactor diode is the special device designed for this purpose. It’s like a tiny, adjustable storage tank for electric charge, controlled by voltage. The other devices, like the tunnel diode or Zener diode, have different jobs and don’t work this way.

\subsubsection{Advanced Explanation}
A varactor diode, also known as a varicap diode, is a semiconductor device specifically engineered to act as a voltage-controlled capacitor. The capacitance of the varactor diode varies with the applied reverse bias voltage. This is due to the change in the width of the depletion region within the diode, which acts as the dielectric in a capacitor. The relationship between the capacitance \( C \) and the applied voltage \( V \) can be approximated by:

\[
C(V) = \frac{C_0}{(1 + \frac{V}{V_0})^n}
\]

where:
\begin{itemize}
    \item \( C_0 \) is the capacitance at zero bias,
    \item \( V_0 \) is the built-in potential of the diode,
    \item \( n \) is a constant that depends on the doping profile of the diode.
\end{itemize}

The varactor diode is widely used in applications such as voltage-controlled oscillators (VCOs), frequency modulators, and tuning circuits in communication systems. In contrast, the tunnel diode is used for high-speed switching, the silicon-controlled rectifier (SCR) is used for power control, and the Zener diode is used for voltage regulation.

% Diagram prompt: Generate a diagram showing the structure of a varactor diode and how the depletion region changes with applied voltage.