\subsection{RF Equipment Exemptions: What You Need to Know!}
\label{sec:E0A09}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=Multiple Choice Question]
    \textbf{E0A09} Which of the following types of equipment are exempt from RF exposure evaluations?
    \begin{enumerate}[label=\Alph*,noitemsep]
        \item Transceivers with less than 7 watts of RF output
        \item Antennas that radiate only in the near field
        \item \textbf{Hand-held transceivers sold before May 3, 2021}
        \item Dish antennas less than one meter in diameter
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a walkie-talkie that you bought before May 3, 2021. The rules say that you don't need to worry about checking how much radio waves it gives off because it's already considered safe. This is like how you don't need to check if your old toy car is safe to play with because it was made before new safety rules came out. So, if you have an old walkie-talkie, you're good to go!

\subsubsection{Advanced Explanation}
RF (Radio Frequency) exposure evaluations are required to ensure that devices emitting radio waves do not pose a health risk to users. However, certain equipment is exempt from these evaluations based on historical safety data and regulatory decisions. 

Hand-held transceivers sold before May 3, 2021, are exempt because they were manufactured and sold under previous regulations that deemed them safe for use without additional exposure evaluations. This exemption is based on the assumption that these devices were designed and tested to meet safety standards in place at the time of their sale.

The other options do not qualify for exemption:
\begin{itemize}
    \item \textbf{A. Transceivers with less than 7 watts of RF output}: While lower power devices generally pose less risk, they are not automatically exempt unless specifically stated by regulations.
    \item \textbf{B. Antennas that radiate only in the near field}: Near-field radiation can still pose exposure risks, and thus, these antennas are not exempt.
    \item \textbf{D. Dish antennas less than one meter in diameter}: The size of the antenna does not inherently exempt it from exposure evaluations.
\end{itemize}

Therefore, the correct answer is \textbf{C. Hand-held transceivers sold before May 3, 2021}.

% Prompt for generating a diagram: A timeline showing the regulatory changes before and after May 3, 2021, with examples of exempt and non-exempt devices.