\subsection{Unlocking the Magic of APRS: What's the Digital Protocol?}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E2D07]
    \textbf{E2D07} What digital protocol is used by APRS?
    \begin{enumerate}[label=\Alph*)]
        \item PACTOR
        \item QAM
        \item \textbf{AX.25}
        \item AMTOR
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
APRS, which stands for Automatic Packet Reporting System, is like a digital messaging system used by ham radio operators to share information like location, weather, and messages. To send this information, APRS uses a specific set of rules or a protocol that ensures the data is sent and received correctly. Think of it like the language that APRS uses to communicate. The correct protocol used by APRS is called AX.25. It’s like the secret handshake that allows APRS devices to talk to each other.

\subsubsection{Advanced Explanation}
APRS operates using the AX.25 protocol, which is a data link layer protocol derived from the X.25 standard. AX.25 is specifically designed for amateur radio use and provides error detection and correction, making it suitable for the often noisy and unreliable radio environment. The protocol handles packet framing, addressing, and flow control, ensuring that data packets are transmitted and received accurately.

To understand why AX.25 is the correct choice, let's briefly examine the other options:
\begin{itemize}
    \item \textbf{PACTOR}: A protocol used for digital communication over HF bands, but not for APRS.
    \item \textbf{QAM (Quadrature Amplitude Modulation)}: A modulation technique, not a protocol, used in various digital communication systems.
    \item \textbf{AMTOR}: A protocol used for error-correcting communication over HF bands, but not for APRS.
\end{itemize}

AX.25 is the backbone of APRS, enabling the transmission of data packets over VHF and UHF frequencies. It uses a combination of bit-oriented framing and CRC (Cyclic Redundancy Check) for error detection, ensuring reliable communication even in challenging conditions.

% Prompt for diagram: A diagram showing the structure of an AX.25 packet and how it is used in APRS communication would be helpful here.