\subsection{FT8 Transceiver Audio Connections}
\label{T4A04}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T4A04]
How are the transceiver audio input and output connected in a station configured to operate using FT8?
\begin{enumerate}[label=\Alph*]
    \item To a computer running a terminal program and connected to a terminal node controller unit
    \item \textbf{To the audio input and output of a computer running WSJT-X software}
    \item To an FT8 conversion unit, a keyboard, and a computer monitor
    \item To a computer connected to the FT8converter.com website
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you’re playing a game on your computer where you need to talk to your friend using a walkie-talkie. But instead of speaking directly into the walkie-talkie, you use your computer to send messages. In FT8, your computer is like the brain that processes the messages, and the walkie-talkie (your transceiver) is just the messenger. So, the audio input and output of your transceiver are connected directly to your computer, which is running special software called WSJT-X. This software helps you send and receive messages in a way that’s super efficient, even if the signal is weak.

\subsubsection{Advanced Explanation}
In a station configured for FT8 operation, the transceiver’s audio input and output are connected to the computer running WSJT-X software. FT8 (Franke-Taylor design, 8-FSK modulation) is a digital mode designed for weak signal communication. The WSJT-X software encodes and decodes the digital signals, which are then transmitted and received by the transceiver. The audio signals are modulated and demodulated by the software, and the transceiver acts as the interface between the computer and the radio frequency (RF) environment. This setup allows for efficient communication over long distances with minimal power.

% Diagram prompt: A diagram showing the connection between the transceiver and the computer, with labels for audio input/output and WSJT-X software.