\subsection{RF Power Meter Installation}
\label{T4A05}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T4A05]
Where should an RF power meter be installed?
\begin{enumerate}[label=\Alph*)]
    \item \textbf{In the feed line, between the transmitter and antenna}
    \item At the power supply output
    \item In parallel with the push-to-talk line and the antenna
    \item In the power supply cable, as close as possible to the radio
\end{enumerate}
\end{tcolorbox}

\subsubsection*{Intuitive Explanation}
Imagine you're trying to measure how much water is flowing through a hose. You wouldn't measure it at the faucet or the nozzle, right? You'd measure it somewhere in the middle of the hose where the water is actually flowing. Similarly, an RF power meter measures the radio frequency (RF) power, so it needs to be placed in the feed line between the transmitter (the faucet) and the antenna (the nozzle). This way, it can accurately measure the power being sent to the antenna.

\subsubsection*{Advanced Explanation}
An RF power meter is designed to measure the power of the radio frequency signal being transmitted. To ensure accurate measurement, it must be installed in the feed line, which is the coaxial cable connecting the transmitter to the antenna. This location allows the meter to measure the forward power (the power being sent from the transmitter to the antenna) and, in some cases, the reflected power (the power being reflected back from the antenna due to impedance mismatch).

The power meter typically uses a directional coupler or a similar device to sample a small portion of the RF signal without significantly affecting the signal's integrity. The sampled signal is then processed to determine the power level. The correct installation point is crucial because measuring at other locations, such as the power supply output or the power supply cable, would not provide meaningful data about the RF power being transmitted.

% Diagram Prompt: Generate a diagram showing the placement of the RF power meter in the feed line between the transmitter and antenna.