\subsection{Power Supply Rating for a 50 Watt FM Transceiver}
\label{T4A01}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T4A01]
Which of the following is an appropriate power supply rating for a typical 50 watt output mobile FM transceiver?
\begin{enumerate}[label=\Alph*)]
    \item 24.0 volts at 4 amperes
    \item 13.8 volts at 4 amperes
    \item 24.0 volts at 12 amperes
    \item \textbf{13.8 volts at 12 amperes}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine your FM transceiver is like a hungry teenager. It needs a certain amount of food (power) to function properly. If you give it too little, it won't work well. If you give it too much, it might get overwhelmed. The question is asking: what's the right amount of food (voltage and current) to keep your transceiver happy and working at its best? The correct answer is like giving it a balanced meal: 13.8 volts and 12 amperes. This combination ensures it has enough energy to output 50 watts without any issues.

\subsubsection{Advanced Explanation}
To determine the appropriate power supply rating, we need to consider the power requirements of the FM transceiver. The power \( P \) in watts can be calculated using the formula:

\[
P = V \times I
\]

where \( V \) is the voltage in volts and \( I \) is the current in amperes. For a 50 watt output transceiver, we need to ensure that the power supply can provide at least 50 watts. Let's evaluate each option:

\begin{itemize}
    \item \textbf{Option A:} \( 24.0 \, \text{V} \times 4 \, \text{A} = 96 \, \text{W} \) (Too high)
    \item \textbf{Option B:} \( 13.8 \, \text{V} \times 4 \, \text{A} = 55.2 \, \text{W} \) (Close, but slightly low)
    \item \textbf{Option C:} \( 24.0 \, \text{V} \times 12 \, \text{A} = 288 \, \text{W} \) (Way too high)
    \item \textbf{Option D:} \( 13.8 \, \text{V} \times 12 \, \text{A} = 165.6 \, \text{W} \) (Sufficient and appropriate)
\end{itemize}

Option D provides more than enough power (165.6 watts) to support the 50 watt output, ensuring the transceiver operates efficiently without being overburdened. Additionally, 13.8 volts is a common voltage rating for mobile transceivers, making it a practical choice.

% Diagram Prompt: A diagram showing the relationship between voltage, current, and power in a simple circuit could help visualize the concept.