\subsection{Computer and Transceiver Connection for Digital Modes}
\label{T4A07}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T4A07]
Which of the following connections is made between a computer and a transceiver to use computer software when operating digital modes?
\begin{enumerate}[label=\Alph*)]
    \item Computer “line out” to transceiver push-to-talk
    \item Computer “line in” to transceiver push-to-talk
    \item \textbf{Computer “line in” to transceiver speaker connector}
    \item Computer “line out” to transceiver speaker connector
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine your computer and transceiver are like two friends trying to talk to each other. The computer wants to send messages (digital modes) to the transceiver, but they need to be connected properly to understand each other. The computer’s “line in” is like its ear, and the transceiver’s speaker connector is like its mouth. So, if you connect the computer’s ear to the transceiver’s mouth, they can have a proper conversation. That’s why the correct connection is “Computer ‘line in’ to transceiver speaker connector.” It’s like making sure your friend’s ear is listening to your mouth!

\subsubsection{Advanced Explanation}
When operating digital modes, the computer generates audio signals that need to be transmitted by the transceiver. The “line in” port on the computer is designed to receive audio signals, while the speaker connector on the transceiver outputs audio signals. By connecting the computer’s “line in” to the transceiver’s speaker connector, the computer can receive the audio signals from the transceiver, process them, and then send the appropriate digital data back to the transceiver for transmission. This setup ensures that the computer can decode and encode digital signals effectively, allowing for seamless communication in digital modes.

% Diagram Prompt: Generate a diagram showing the connection between a computer and a transceiver, highlighting the line in and speaker connector ports.