\subsection{Who's in Charge? A Guide to Amateur Operator Exam Supervision!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E1E06] Who is responsible for the proper conduct and necessary supervision during an amateur operator license examination session?
    \begin{enumerate}[label=\Alph*),noitemsep]
        \item The VEC coordinating the session
        \item The designated monitoring VE
        \item \textbf{Each administering VE}
        \item Only the VE session manager
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you are taking a test at school. There are several teachers in the room making sure everything goes smoothly. Each teacher has a specific job to do, like handing out papers, watching for cheating, and answering questions. In the same way, during an amateur radio operator exam, each person who is administering the test (called a Volunteer Examiner or VE) is responsible for making sure the test is fair and runs properly. It’s not just one person’s job; everyone has to do their part to make sure the test is conducted correctly.

\subsubsection{Advanced Explanation}
In the context of amateur radio licensing exams, the responsibility for the proper conduct and supervision of the examination session is distributed among all the administering Volunteer Examiners (VEs). According to the Federal Communications Commission (FCC) rules and the guidelines provided by the Volunteer Examiner Coordinator (VEC), each VE is accountable for ensuring the integrity of the examination process. This includes verifying the identity of the candidates, maintaining the security of the exam materials, and ensuring that the examination is conducted in a fair and impartial manner. The VEC coordinates the session, but the actual supervision and conduct of the exam are the responsibilities of the VEs. The designated monitoring VE and the VE session manager have specific roles, but the overall responsibility is shared by all administering VEs.

% Diagram prompt: Generate a diagram showing the hierarchy of responsibilities during an amateur operator license examination session, highlighting the roles of the VEC, VEs, and candidates.