\subsection{Next Steps for VE Team After a Successful Exam!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E1E11] What must the VE team do if an examinee scores a passing grade on all examination elements needed for an upgrade or new license?
    \begin{enumerate}[label=\Alph*]
        \item Photocopy all examination documents and forward them to the FCC for processing
        \item \textbf{Three VEs must certify that the examinee is qualified for the license grant and that they have complied with the administering VE requirements}
        \item Issue the examinee the new or upgrade license
        \item All these choices are correct
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you’ve just taken a test to get a new or upgraded license, like a driver’s license but for using radios. If you pass all the parts of the test, the people who gave you the test (the VE team) have to make sure everything is done correctly. They don’t just give you the license right away. Instead, three of them need to check and confirm that you really passed and that they followed all the rules while giving the test. It’s like having three teachers check your test to make sure everything is fair and correct before you get your license.

\subsubsection{Advanced Explanation}
When an examinee successfully passes all elements of an amateur radio license examination, the Volunteer Examiners (VEs) have specific responsibilities to ensure compliance with Federal Communications Commission (FCC) regulations. According to FCC rules, three VEs must certify that the examinee has met the necessary qualifications for the license grant. This certification includes verifying that the examinee has passed all required examination elements and that the VEs have adhered to all administering VE requirements. This process ensures the integrity and validity of the examination process. The VEs do not issue the license directly; instead, they submit the necessary documentation to the FCC, which then grants the license. This step-by-step verification process is crucial to maintaining the standards of amateur radio licensing.

% Prompt for generating a diagram: A flowchart showing the steps from examinee passing the test to the FCC granting the license, highlighting the role of the three VEs in certification.