\subsection{Ripple and Sharp Cutoff: The Filter Fun!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E7C05] Which filter type has ripple in the passband and a sharp cutoff?
    \begin{enumerate}[label=\Alph*]
        \item A Butterworth filter
        \item An active LC filter
        \item A passive op-amp filter
        \item \textbf{A Chebyshev filter}
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you are listening to music on your headphones, and you want to make sure that only the sounds you like get through. Some filters let all the sounds pass smoothly, but others might let some extra bumps or ripples in the sound you want. However, these filters can also stop the sounds you don't want very sharply, like a knife cutting through butter. The Chebyshev filter is like this—it lets some ripples in the sounds you want but stops the unwanted sounds very sharply.

\subsubsection{Advanced Explanation}
The Chebyshev filter is a type of filter that is designed to achieve a sharp cutoff between the passband and the stopband. This is accomplished by allowing some ripple in the passband, which is a small variation in the amplitude of the signal within the passband. The amount of ripple can be controlled by the filter design parameters. The Chebyshev filter is characterized by its equiripple behavior in the passband and its steep roll-off in the stopband.

Mathematically, the magnitude response of a Chebyshev filter is given by:
\[
|H(j\omega)| = \frac{1}{\sqrt{1 + \epsilon^2 T_n^2(\omega/\omega_c)}}
\]
where:
\begin{itemize}
    \item \( \epsilon \) is the ripple factor,
    \item \( T_n \) is the Chebyshev polynomial of order \( n \),
    \item \( \omega \) is the angular frequency,
    \item \( \omega_c \) is the cutoff frequency.
\end{itemize}

The Chebyshev filter is particularly useful in applications where a sharp transition between the passband and stopband is required, even if it means tolerating some ripple in the passband. This makes it a popular choice in RF and audio applications where precise frequency control is necessary.

% Diagram Prompt: Generate a diagram showing the magnitude response of a Chebyshev filter compared to a Butterworth filter, highlighting the ripple in the passband and the sharp cutoff.