\subsection{Types of Amateur Stations for Automatic Retransmission}
\label{T1D07}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T1D07]
What types of amateur stations can automatically retransmit the signals of other amateur stations?
\begin{enumerate}[label=\Alph*]
    \item Auxiliary, beacon, or Earth stations
    \item Earth, repeater, or space stations
    \item Beacon, repeater, or space stations
    \item \textbf{Repeater, auxiliary, or space stations}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a walkie-talkie, and you want to send a message to your friend who is far away. But your walkie-talkie can't reach that far. So, you use a special station called a repeater that listens to your message and then sends it again, louder and stronger, so your friend can hear it. There are also other types of stations like auxiliary and space stations that can do similar things. So, the correct answer is the one that includes all these helpful stations: repeater, auxiliary, and space stations.

\subsubsection{Advanced Explanation}
In amateur radio, certain types of stations are designed to automatically retransmit signals to extend the range or improve the quality of communication. These stations include:

\begin{itemize}
    \item \textbf{Repeater Stations}: These are fixed stations that receive signals on one frequency and retransmit them on another frequency, often with higher power, to cover a larger area.
    \item \textbf{Auxiliary Stations}: These are secondary stations that assist primary stations by retransmitting signals, often used in conjunction with repeaters.
    \item \textbf{Space Stations}: These are stations located on satellites or other space objects that retransmit signals from Earth, enabling long-distance communication.
\end{itemize}

The correct answer, therefore, is \textbf{D: Repeater, auxiliary, or space stations}, as these are the types of amateur stations that can automatically retransmit the signals of other amateur stations.

% Diagram prompt: Generate a diagram showing the flow of signals from an amateur station to a repeater, auxiliary, and space station, and then to the receiving station.