\subsection{Unlocking Circuit Secrets: Exploring Frequency Response with a Capacitor!}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=E7G02] What is the frequency response of the circuit in E7-3 if a capacitor is added across the feedback resistor?
    \begin{enumerate}[label=\Alph*),noitemsep]
        \item High-pass filter
        \item \textbf{Low-pass filter}
        \item Band-pass filter
        \item Notch filter
    \end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a circuit that controls how different frequencies of sound pass through it. If you add a capacitor across the feedback resistor, it’s like adding a gate that lets low-pitched sounds (low frequencies) pass through easily but blocks high-pitched sounds (high frequencies). This is because the capacitor slows down the high frequencies, making it harder for them to get through. So, the circuit becomes a low-pass filter, allowing only the low frequencies to pass.

\subsubsection{Advanced Explanation}
When a capacitor is added across the feedback resistor in an operational amplifier (op-amp) circuit, it introduces a frequency-dependent impedance. The impedance of a capacitor \( Z_C \) is given by:
\[
Z_C = \frac{1}{j\omega C}
\]
where \( \omega \) is the angular frequency and \( C \) is the capacitance. At low frequencies, the impedance of the capacitor is high, and the feedback is primarily through the resistor, allowing the signal to pass. At high frequencies, the impedance of the capacitor decreases, effectively shorting the feedback resistor and reducing the gain of the amplifier. This behavior characterizes a low-pass filter, which attenuates high frequencies while allowing low frequencies to pass.

The cutoff frequency \( f_c \) of the low-pass filter can be calculated using:
\[
f_c = \frac{1}{2\pi R_f C}
\]
where \( R_f \) is the feedback resistor and \( C \) is the capacitance. This equation shows how the values of the resistor and capacitor determine the frequency at which the filter starts to attenuate the signal.

% Prompt for generating a diagram: 
% Diagram showing an operational amplifier circuit with a feedback resistor and a capacitor connected in parallel across the resistor. Label the components and indicate the input and output signals.