\subsection{Supported Operating Activities in WSJT-X}
\label{T8D10}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T8D10]
Which of the following operating activities is supported by digital mode software in the WSJT-X software suite?
\begin{enumerate}[label=\Alph*)]
    \item Earth-Moon-Earth
    \item Weak signal propagation beacons
    \item Meteor scatter
    \item \textbf{All these choices are correct}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a super cool app on your phone that lets you do all sorts of fun things like sending messages to the moon, finding really faint signals, and even bouncing signals off meteors. WSJT-X is like that app but for ham radio operators. It supports all these awesome activities, so you don’t need to pick just one—you can do them all!

\subsubsection{Advanced Explanation}
The WSJT-X software suite is a powerful tool for amateur radio operators, particularly for digital modes that require precise timing and signal processing. It supports a variety of operating activities, including:

\begin{itemize}
    \item \textbf{Earth-Moon-Earth (EME)}: This involves bouncing radio signals off the moon to communicate with other stations. WSJT-X provides the necessary tools for weak signal detection and decoding, which is crucial for EME communications.
    \item \textbf{Weak Signal Propagation Beacons}: These are used to study the propagation of radio signals under weak signal conditions. WSJT-X can decode these beacons, allowing operators to analyze propagation paths.
    \item \textbf{Meteor Scatter}: This technique uses the ionized trails left by meteors to reflect radio signals. WSJT-X includes modes specifically designed for meteor scatter communications, enabling brief but effective contacts.
\end{itemize}

The correct answer is \textbf{D}, as WSJT-X supports all these activities, making it a versatile tool for amateur radio operators engaged in various forms of weak signal communication.

% Diagram prompt: Generate a diagram showing the different operating activities supported by WSJT-X, such as EME, weak signal propagation beacons, and meteor scatter.