\subsection{Understanding Picofarads and Microfarads}
\label{T5B08}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=T5B08]
Which is equal to 1,000,000 picofarads?
\begin{enumerate}[label=\Alph*)]
    \item 0.001 microfarads
    \item \textbf{1 microfarad}
    \item 1000 microfarads
    \item 1,000,000,000 microfarads
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a tiny bucket called a picofarad. Now, if you have a million of these tiny buckets, how many bigger buckets called microfarads would you have? Well, it turns out that one microfarad is like a big bucket that can hold a million tiny picofarad buckets! So, 1,000,000 picofarads is the same as 1 microfarad. Easy, right?

\subsubsection{Advanced Explanation}
To understand this question, we need to know the relationship between picofarads (pF) and microfarads ($\mu$F). The prefix pico means $10^{-12}$, and micro means $10^{-6}$. Therefore, 1 picofarad is equal to $10^{-12}$ farads, and 1 microfarad is equal to $10^{-6}$ farads.

To convert 1,000,000 picofarads to microfarads, we can use the following steps:

1. Start with 1,000,000 picofarads.
2. Convert picofarads to farads: $1,000,000 \text{ pF} = 1,000,000 \times 10^{-12} \text{ F} = 10^{-6} \text{ F}$.
3. Convert farads to microfarads: $10^{-6} \text{ F} = 1 \mu\text{F}$.

Thus, 1,000,000 picofarads is equal to 1 microfarad.

% Diagram Prompt: A diagram showing the conversion from picofarads to microfarads with a visual representation of the scale difference could be helpful here.