\subsection{Maximum Bandwidth for USB Transmissions in the 60-Meter Band}\label{G1C03}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G1C03]
What is the maximum bandwidth permitted by FCC rules for amateur radio stations transmitting on USB frequencies in the 60-meter band?
\begin{enumerate}[label=\Alph*)]
    \item \textbf{2.8 kHz}
    \item 5.6 kHz
    \item 1.8 kHz
    \item 3 kHz
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you’re trying to talk to your friend on a walkie-talkie, but there’s only a small lane for your voice to travel through. The FCC (the people who make the rules for radios) says that on the 60-meter band, your voice can only take up a tiny space—specifically, 2.8 kHz wide. Think of it like a narrow road where only one car (your voice) can fit at a time. If your voice were any wider, it would bump into other people’s voices, and no one would understand anything!

\subsubsection{Advanced Explanation}
The 60-meter band (5.3–5.4 MHz) is a unique amateur radio band where specific rules apply to ensure efficient use of the spectrum. The FCC restricts the maximum bandwidth for USB (Upper Sideband) transmissions to 2.8 kHz. This limitation is imposed to minimize interference with other users of the band and to ensure that the signal remains within the allocated frequency range.

Bandwidth refers to the range of frequencies occupied by a signal. For USB transmissions, the bandwidth is determined by the highest frequency component of the modulating signal. Mathematically, the bandwidth \( B \) can be expressed as:
\[
B = f_{\text{max}} - f_{\text{min}}
\]
where \( f_{\text{max}} \) and \( f_{\text{min}} \) are the highest and lowest frequencies of the signal, respectively. In this case, the FCC mandates that \( B \leq 2.8 \) kHz.

This restriction ensures that amateur radio operators can communicate effectively without causing undue interference to other services sharing the band. Understanding bandwidth and its regulation is crucial for compliance with FCC rules and for optimizing radio communication.

% Prompt for diagram: A diagram showing the frequency spectrum of the 60-meter band with the 2.8 kHz bandwidth marked for USB transmissions would be helpful here.