\subsection{FCC Rules for Operating in the 60-Meter Band}
\label{G1C04}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G1C04]
Which of the following is required by the FCC rules when operating in the 60-meter band?
\begin{enumerate}[label=\Alph*,noitemsep]
    \item \textbf{If you are using an antenna other than a dipole, you must keep a record of the gain of your antenna}
    \item You must keep a record of the date, time, frequency, power level, and stations worked
    \item You must keep a record of all third-party traffic
    \item You must keep a record of the manufacturer of your equipment and the antenna used
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're playing a game where you have to follow certain rules to make sure everyone is playing fair. In the 60-meter band, the FCC (the rule-makers) want to make sure that if you're using a fancy antenna (not just a simple dipole), you need to keep track of how much extra boost it gives you. This way, everyone knows you're not cheating by using an antenna that gives you an unfair advantage. It's like keeping a scorecard for your antenna's performance!

\subsubsection{Advanced Explanation}
The 60-meter band is a specific frequency range allocated for amateur radio use, and the FCC has established rules to ensure proper operation within this band. One of these rules pertains to the use of antennas. A dipole antenna is a standard, balanced antenna that is commonly used in amateur radio. However, if an operator chooses to use a different type of antenna, such as a directional antenna with gain, the FCC requires that the operator maintain a record of the antenna's gain.

Antenna gain is a measure of how effectively an antenna directs or concentrates radio frequency energy in a particular direction compared to a reference antenna, typically a dipole. The gain is usually expressed in decibels (dB). By keeping a record of the antenna gain, the FCC ensures that operators are not exceeding the allowed power limits when using antennas that can focus energy more efficiently.

Mathematically, the effective radiated power (ERP) can be calculated using the formula:
\[
\text{ERP} = P_{\text{transmitter}} \times G_{\text{antenna}}
\]
where \( P_{\text{transmitter}} \) is the power output of the transmitter and \( G_{\text{antenna}} \) is the gain of the antenna. By recording the antenna gain, operators can verify that their ERP remains within the legal limits set by the FCC.

This rule helps maintain a level playing field and ensures that all operators are adhering to the same standards, preventing any single operator from gaining an unfair advantage through the use of high-gain antennas.

% Prompt for generating a diagram: A diagram showing a comparison between a dipole antenna and a directional antenna with gain, illustrating the concept of antenna gain and how it affects the radiation pattern.