\subsection{Permitted One-Way Transmissions}\label{G1B05}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G1B05]
Which of the following one-way transmissions are permitted?
\begin{enumerate}[label=\Alph*),noitemsep]
    \item Unidentified test transmissions of less than 10 seconds in duration
    \item \textbf{Transmissions to assist with learning the International Morse code}
    \item Regular transmissions offering equipment for sale, if intended for amateur radio use
    \item All these choices are correct
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you're learning to play a new instrument, like the guitar. You need to practice, right? Similarly, when learning Morse code, you need to practice sending and receiving those dots and dashes. The rules say it's okay to send one-way transmissions (like a teacher sending Morse code to a student) to help with learning. So, option B is like your guitar teacher playing a chord for you to copy. The other options? They’re like playing random notes or trying to sell your guitar during a lesson—not allowed!

\subsubsection{Advanced Explanation}
In amateur radio, one-way transmissions are generally restricted to prevent misuse, such as broadcasting or unauthorized communications. However, certain exceptions exist under the regulations. One such exception is transmissions intended to assist in learning the International Morse code. This is permitted because it serves an educational purpose and does not interfere with normal communication protocols.

The other options are not permitted for the following reasons:
\begin{itemize}
    \item \textbf{Option A}: Unidentified test transmissions, even if brief, are not allowed because they lack transparency and could cause confusion or interference.
    \item \textbf{Option C}: Regular transmissions offering equipment for sale are considered commercial activities, which are prohibited in amateur radio.
    \item \textbf{Option D}: Since options A and C are not permitted, this option is incorrect.
\end{itemize}

Thus, the correct answer is \textbf{B}, as it aligns with the regulatory exceptions for one-way transmissions in amateur radio.

% Prompt for diagram: A flowchart showing permitted vs. non-permitted one-way transmissions in amateur radio could help visualize the distinctions.