\subsection{Precautions Before Climbing a Tower}\label{G0B08}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G0B08]
What should be done before climbing a tower that supports electrically powered devices?
\begin{enumerate}[label=\Alph*)]
    \item Notify the electric company that a person will be working on the tower
    \item \textbf{Make sure all circuits that supply power to the tower are locked out and tagged}
    \item Unground the base of the tower
    \item All these choices are correct
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you’re about to climb a giant jungle gym, but this jungle gym is also a giant lightning rod with electricity running through it. Would you just start climbing without making sure the electricity is turned off? Of course not! That’s why, before you climb, you need to make sure all the power to the tower is locked out and tagged. This is like putting a big DO NOT TOUCH sign on the power switch so no one accidentally turns it on while you’re up there. Safety first!

\subsubsection{Advanced Explanation}
Before climbing a tower that supports electrically powered devices, it is crucial to ensure that all electrical circuits supplying power to the tower are locked out and tagged. This process, known as Lockout/Tagout (LOTO), is a safety procedure used in industry to ensure that dangerous machines are properly shut off and not started up again before the completion of maintenance or servicing work. 

The steps involved in LOTO are:
\begin{enumerate}
    \item Identify all energy sources connected to the tower.
    \item Shut down the equipment and disconnect it from the energy source.
    \item Apply lockout devices to each energy source to prevent re-energization.
    \item Attach a tag to each lockout device indicating that the equipment should not be operated.
\end{enumerate}

This procedure is essential to prevent accidental energization, which could lead to severe electrical hazards, including electric shock, arc flash, or even electrocution. The correct answer, therefore, is to make sure all circuits that supply power to the tower are locked out and tagged.

% Prompt for diagram: A diagram showing the steps of the Lockout/Tagout (LOTO) procedure would be helpful here.