\subsection{Fuse or Circuit Breaker Sizing for AWG 14 Wiring}
\label{G0B03}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G0B03]
Which size of fuse or circuit breaker would be appropriate to use with a circuit that uses AWG number 14 wiring?
\begin{enumerate}[label=\Alph*]
    \item 30 amperes
    \item 25 amperes
    \item 20 amperes
    \item \textbf{15 amperes}
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you have a water pipe that can only handle a certain amount of water flowing through it without bursting. If you try to push too much water through, the pipe will break. Similarly, electrical wires can only handle a certain amount of current before they get too hot and could start a fire. AWG 14 wire is like a medium-sized pipe—it can handle up to 15 amperes of current safely. If you use a fuse or circuit breaker that allows more than 15 amperes, it’s like trying to push too much water through the pipe, and that’s dangerous! So, the correct choice is 15 amperes.

\subsubsection{Advanced Explanation}
The American Wire Gauge (AWG) system standardizes wire sizes, with smaller AWG numbers indicating thicker wires. AWG 14 wire has a diameter of approximately 1.63 mm and is commonly used in residential wiring. The National Electrical Code (NEC) specifies that AWG 14 copper wire can safely carry up to 15 amperes of current when used in a circuit with a 60°C insulation rating. 

The relationship between wire size and current capacity is governed by Ohm's Law and the wire's resistance. The resistance \( R \) of a wire is given by:
\[ R = \rho \frac{L}{A} \]
where \( \rho \) is the resistivity of the material, \( L \) is the length of the wire, and \( A \) is the cross-sectional area. For AWG 14 copper wire, the resistance is approximately 2.58 ohms per 1000 feet.

The power dissipated in the wire due to current \( I \) is:
\[ P = I^2 R \]
Exceeding the current rating increases \( P \), leading to excessive heat and potential fire hazards. Therefore, a 15-ampere fuse or circuit breaker is appropriate to protect AWG 14 wiring, ensuring the current does not exceed the wire's safe capacity.

% Diagram Prompt: Generate a diagram showing the relationship between wire gauge (AWG) and current capacity, highlighting AWG 14 and its 15-ampere limit.