\subsection{Fusing in a 240 VAC Circuit}
\label{G0B01}

\begin{tcolorbox}[colback=gray!10!white,colframe=black!75!black,title=G0B01]
Which wire or wires in a four-conductor 240 VAC circuit should be attached to fuses or circuit breakers?
\begin{enumerate}[label=\Alph*,noitemsep]
    \item \textbf{Only the hot wires}
    \item Only the neutral wire
    \item Only the ground wire
    \item All wires
\end{enumerate}
\end{tcolorbox}

\subsubsection{Intuitive Explanation}
Imagine you’re at a water park, and there are two big slides (the hot wires) that bring water down to the pool (your appliances). The neutral wire is like the drain that takes the water back to the start, and the ground wire is like a safety net in case something goes wrong. Now, if you want to control the water flow and make sure it doesn’t get too crazy, you’d put a valve (fuse or circuit breaker) on the slides, not the drain or the safety net. That’s why only the hot wires need fuses or circuit breakers—they’re the ones carrying the power that needs to be controlled.

\subsubsection{Advanced Explanation}
In a 240 VAC circuit, the hot wires (often referred to as Line 1 and Line 2) carry the electrical current from the power source to the load. The neutral wire provides a return path for the current, and the ground wire is a safety feature that provides a path to earth in case of a fault. 

Fuses and circuit breakers are designed to protect the circuit from overcurrent conditions, which can lead to overheating and potentially cause fires. Since the hot wires are the ones carrying the current, they are the ones that need to be protected. The neutral wire does not carry current under normal conditions, and the ground wire only carries current in the event of a fault. Therefore, fuses or circuit breakers should only be installed on the hot wires.

Mathematically, the current \( I \) in a circuit is given by Ohm's Law:
\[
I = \frac{V}{R}
\]
where \( V \) is the voltage and \( R \) is the resistance. In a 240 VAC circuit, the voltage across the hot wires is 240 V, and the current flows through these wires to the load. Protecting these wires ensures that the current does not exceed the safe limits of the circuit components.

% Diagram prompt: Generate a diagram showing a 240 VAC circuit with two hot wires, a neutral wire, and a ground wire, with fuses or circuit breakers on the hot wires.